---
title: "01_build_investment_data"
author: "Joep Keuzenkamp"
date: "2025-01-10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Geographic regions

Here, we lay the groundwork by providing all the geographic regions in the dataset.

```{r}
# Add the census tracts
census_tracts <- sf::st_read("Data/raw data/tlgdb_2020_a_us_substategeo.gdb", layer = "Census_Tract")
census_tracts <- census_tracts %>%
  select("GEOID", "NAMELSAD", "SHAPE") %>%
  rename("census_tract_id" = "GEOID",
         "census_tract_name" = "NAMELSAD")
census_tracts$county_id <- str_sub(census_tracts$census_tract_id, 1, 5)
census_tracts$state_id <- str_sub(census_tracts$census_tract_id, 1, 2)
counties <- sf::st_read("Data/raw data/tlgdb_2020_a_us_substategeo.gdb", layer = "County")
counties <- counties %>%
  select("GEOID", "NAMELSAD") %>%
  rename("county_id" = "GEOID",
         "county_name" = "NAMELSAD") %>%
  st_drop_geometry()
census_tracts <- left_join(census_tracts, counties, by = "county_id")

rm(counties)
```

## Add the 2023 (cohort 1) energy communities: IRS notice 2023-29

```{r}
coal_closure <- read.csv("Data/raw data/IRA_Coal_Closure_Energy_Comm_2023v2/Coal_Closure_Energy_Communities_2023v2.csv")
coal_closure$geoid_tract_2020 <- str_pad(coal_closure$geoid_tract_2020, 11, pad = "0")
EC_employ <- read.csv("Data/raw data/MSA_NMSA_FEE_EC_Status_2023v2/MSA_NMSA_FFE_EC_2023v2.csv")
EC_employ$geoid_cty_2020 <- str_pad(EC_employ$geoid_cty_2020, 5, pad = "0")
coal_closure_mine <- coal_closure %>%
  filter(Tract_Status %in% c("is an energy community due to a coal mine closure"))
coal_closure_mine <- unique(coal_closure_mine$geoid_tract_2020)
coal_closure_generator <- coal_closure %>%
  filter(Generator_Closure == "Yes")
coal_closure_generator <- unique(coal_closure_generator$geoid_tract_2020)
coal_closure_adjacent <- coal_closure %>%
  filter(Adjacent_to_Closure == "Yes")
coal_closure_adjacent <- unique(coal_closure_adjacent$geoid_tract_2020)
EC_employ <- unique(EC_employ[EC_employ$EC_qual_status == "Yes", ]$geoid_cty_2020)

data <- census_tracts

data$coal_mine_closure_official_cohort_1 <- ifelse(data$census_tract_id %in% coal_closure_mine, 1, 0)
data$generator_closure_official_cohort_1 <- ifelse(data$census_tract_id %in% coal_closure_generator, 1, 0)
data$adjacent_closure_official_cohort_1 <- ifelse(data$census_tract_id %in% coal_closure_adjacent, 1, 0)
data$unemployment_official_msa_cohort_1 <- ifelse(data$county_id %in% EC_employ, 1, 0)

rm(coal_closure, EC_employ, coal_closure_adjacent, coal_closure_generator, coal_closure_mine)
```

## Add the 2023 (cohort 2) energy communities: IRS notice 2024-30

```{r}
coal_closure <- read.csv("Data/raw data/IRA_Coal_Closure_Energy_Comm_2023v2/Coal_Closure_Energy_Communities_2023v2.csv")
coal_closure$geoid_tract_2020 <- str_pad(coal_closure$geoid_tract_2020, 11, pad = "0")
EC_employ <- read.csv("Data/raw data/MSA_NMSA_EC_FFE_Status_v2023_3/MSA_NonMSA_EnergyCommunities_FossilFuelEmp_2023v3.csv")
EC_employ$geoid_county_2020 <- str_pad(EC_employ$geoid_county_2020, 5, pad = "0")
coal_closure_mine <- coal_closure %>%
  filter(Tract_Status %in% c("is an energy community due to a coal mine closure"))
coal_closure_mine <- unique(coal_closure_mine$geoid_tract_2020)
coal_closure_generator <- coal_closure %>%
  filter(Generator_Closure == "Yes")
coal_closure_generator <- unique(coal_closure_generator$geoid_tract_2020)
coal_closure_adjacent <- coal_closure %>%
  filter(Adjacent_to_Closure == "Yes")
coal_closure_adjacent <- unique(coal_closure_adjacent$geoid_tract_2020)
EC_employ <- unique(EC_employ[EC_employ$ec_qual_status == "Yes", ]$geoid_county_2020)

data$coal_mine_closure_official_cohort_2 <- ifelse(data$census_tract_id %in% coal_closure_mine, 1, 0)
data$generator_closure_official_cohort_2 <- ifelse(data$census_tract_id %in% coal_closure_generator, 1, 0)
data$adjacent_closure_official_cohort_2 <- ifelse(data$census_tract_id %in% coal_closure_adjacent, 1, 0)
data$unemployment_official_msa_cohort_2 <- ifelse(data$county_id %in% EC_employ, 1, 0)

rm(coal_closure, EC_employ, coal_closure_adjacent, coal_closure_generator, coal_closure_mine)
```

## Add the 2024 (cohort 3) energy communities: IRS notice 2024-48

```{r}
coal_closure <- read.csv("Data/raw data/Coal_Closures_EnergyComm_v2024_1/IRA_EnergyComm_CTracts_CoalClosures_v2024_1.csv")
coal_closure$geoid_tract_2020 <- str_pad(coal_closure$geoid_tract_2020, 11, pad = "0")
EC_employ <- read.csv("Data/raw data/MSA_NMSA_EC_FFE_v2024_1/MSA_NonMSA_EnergyCommunities_FossilFuelEmp_v2024_1.csv")
EC_employ$geoid_county_2020 <- str_pad(EC_employ$geoid_county_2020, 5, pad = "0")
coal_closure_mine <- coal_closure %>%
  filter(Mine_Closure == "Yes")
coal_closure_mine <- unique(coal_closure_mine$geoid_tract_2020)
coal_closure_generator <- coal_closure %>%
  filter(Generator_Closure == "Yes")
coal_closure_generator <- unique(coal_closure_generator$geoid_tract_2020)
coal_closure_adjacent <- coal_closure %>%
  filter(Adjacent_to_Closure == "Yes")
coal_closure_adjacent <- unique(coal_closure_adjacent$geoid_tract_2020)
EC_employ <- unique(EC_employ[EC_employ$ec_qual_status == "Yes", ]$geoid_county_2020)

data$coal_mine_closure_official_cohort_3 <- ifelse(data$census_tract_id %in% coal_closure_mine, 1, 0)
data$generator_closure_official_cohort_3 <- ifelse(data$census_tract_id %in% coal_closure_generator, 1, 0)
data$adjacent_closure_official_cohort_3 <- ifelse(data$census_tract_id %in% coal_closure_adjacent, 1, 0)
data$unemployment_official_msa_cohort_3 <- ifelse(data$county_id %in% EC_employ, 1, 0)

rm(coal_closure, EC_employ, coal_closure_adjacent, coal_closure_generator, coal_closure_mine)
```

## Add binary indicator for energy communities

```{r}
data <- data %>%
  mutate(ec_ind_official_cohort_1 = ifelse((coal_mine_closure_official_cohort_1 == 1 | 
                                   generator_closure_official_cohort_1 == 1 | 
                                   adjacent_closure_official_cohort_1 == 1) |
                                   unemployment_official_msa_cohort_1 == 1, 
                                   1, 0))

data <- data %>%
  mutate(ec_ind_official_cohort_2 = ifelse((coal_mine_closure_official_cohort_2 == 1 | 
                                   generator_closure_official_cohort_2 == 1 | 
                                   adjacent_closure_official_cohort_2 == 1) |
                                   unemployment_official_msa_cohort_2 == 1, 
                                   1, 0))

data <- data %>%
  mutate(ec_ind_official_cohort_3 = ifelse((coal_mine_closure_official_cohort_3 == 1 | 
                                   generator_closure_official_cohort_3 == 1 | 
                                   adjacent_closure_official_cohort_3 == 1) |
                                   unemployment_official_msa_cohort_3 == 1, 
                                   1, 0))
```

## Make a timeseries dataframe

```{r}
# We should have a row for each quarter-census tract combination
quarters <- seq.Date(from = as.Date("2018-01-01"), to = as.Date("2024-12-31"), by = "quarter")
census_tracts <- unique(data$census_tract_id)
all_combinations <- expand.grid(census_tract_id = census_tracts, quarter_date = quarters)
data <- merge(all_combinations, data, by = "census_tract_id", all.x = TRUE)
data$year <- substr(data$quarter, 1, 4)
data <- data %>%
  mutate(quarter = quarters(quarter_date))

rm(census_tracts, all_combinations, quarters)
```

## Prepare the investment dataset and generate some statistics

```{r}
investment <- read.csv("Data/raw data/CIM/manufacturing_energy_and_industry_facility_metadata.csv", skip = 5)

# Create a couple of date variables
investment$Announcement_Date <- as.Date(investment$Announcement_Date)
investment <- investment %>%
  mutate(quarter = quarters(Announcement_Date),
         year = year(Announcement_Date))
investment <- investment[as.numeric(investment$year) > 2017, ]  

investment_solar <- investment %>% 
  filter(Segment == "Energy and Industry") %>%
  filter(Technology == "Solar")

investment_wind <- investment %>% 
  filter(Segment == "Energy and Industry") %>%
  filter(Technology == "Wind")

# Adjust investment numbers
investment <- investment %>%
  mutate(Estimated_Total_Facility_CAPEX = as.numeric(as.character(Estimated_Total_Facility_CAPEX)))
investment$Estimated_Total_Facility_CAPEX <- investment$Estimated_Total_Facility_CAPEX * 1e6

investment$census_tract_2020_geoid <- as.factor(investment$census_tract_2020_geoid)

rm(investment_solar, investment_wind)
```

## Add the sum of investment for solar

```{r}
solar_investment <- investment %>%
  filter(Technology == "Solar" & Segment == "Energy and Industry" & Current_Facility_Status %in% c("Under Construction", "Operating", "Announced")) %>%
  select(year, quarter, census_tract_2020_geoid, Estimated_Total_Facility_CAPEX) %>%
  group_by(census_tract_2020_geoid, year, quarter) %>%
  summarise(investment_solar = sum(Estimated_Total_Facility_CAPEX, na.rm = TRUE)) %>%
  ungroup() %>%
  rename("census_tract_id" = "census_tract_2020_geoid")

data$year <- as.numeric(data$year)

data <- left_join(data, solar_investment, by = c("census_tract_id", "year", "quarter"))
data$investment_solar <- ifelse(is.na(data$investment_solar), 0, data$investment_solar)

solar_investment <- investment %>%
  filter(Technology == "Solar" & Segment == "Energy and Industry" & Current_Facility_Status %in% c("Under Construction")) %>%
  select(year, quarter, census_tract_2020_geoid, Estimated_Total_Facility_CAPEX) %>%
  group_by(census_tract_2020_geoid, year, quarter) %>%
  summarise(investment_solar_under_construction = sum(Estimated_Total_Facility_CAPEX, na.rm = TRUE)) %>%
  ungroup() %>%
  rename("census_tract_id" = "census_tract_2020_geoid")

data <- left_join(data, solar_investment, by = c("census_tract_id", "year", "quarter"))
data$investment_solar_under_construction <- ifelse(is.na(data$investment_solar_under_construction), 0, data$investment_solar_under_construction)

solar_investment <- investment %>%
  filter(Technology == "Solar" & Segment == "Energy and Industry" & Current_Facility_Status %in% c("Operating")) %>%
  select(year, quarter, census_tract_2020_geoid, Estimated_Total_Facility_CAPEX) %>%
  group_by(census_tract_2020_geoid, year, quarter) %>%
  summarise(investment_solar_operating = sum(Estimated_Total_Facility_CAPEX, na.rm = TRUE)) %>%
  ungroup() %>%
  rename("census_tract_id" = "census_tract_2020_geoid")

data <- left_join(data, solar_investment, by = c("census_tract_id", "year", "quarter"))
data$investment_solar_operating <- ifelse(is.na(data$investment_solar_operating), 0, data$investment_solar_operating)

solar_investment <- investment %>%
  filter(Technology == "Solar" & Segment == "Energy and Industry" & Current_Facility_Status %in% c("Announced")) %>%
  select(year, quarter, census_tract_2020_geoid, Estimated_Total_Facility_CAPEX) %>%
  group_by(census_tract_2020_geoid, year, quarter) %>%
  summarise(investment_solar_announced = sum(Estimated_Total_Facility_CAPEX, na.rm = TRUE)) %>%
  ungroup() %>%
  rename("census_tract_id" = "census_tract_2020_geoid")

data <- left_join(data, solar_investment, by = c("census_tract_id", "year", "quarter"))
data$investment_solar_announced <- ifelse(is.na(data$investment_solar_announced), 0, data$investment_solar_announced)

rm(solar_investment)
```

## Add the sum of investment for wind

```{r}
wind_investment <- investment %>%
  filter(Technology == "Wind" & Segment == "Energy and Industry" & Current_Facility_Status %in% c("Under Construction", "Operating", "Announced")) %>%
  select(year, quarter, census_tract_2020_geoid, Estimated_Total_Facility_CAPEX) %>%
  group_by(census_tract_2020_geoid, year, quarter) %>%
  summarise(investment_wind = sum(Estimated_Total_Facility_CAPEX, na.rm = TRUE)) %>%
  ungroup() %>%
  rename("census_tract_id" = "census_tract_2020_geoid")

data <- left_join(data, wind_investment, by = c("census_tract_id", "year", "quarter"))
data$investment_wind <- ifelse(is.na(data$investment_wind), 0, data$investment_wind)

rm(wind_investment)
```

## Add small and large solar and wind investment separately

```{r}
solar_investment <- investment %>%
  filter(Technology == "Solar" & Segment == "Energy and Industry" & Current_Facility_Status %in% c("Under Construction", "Operating", "Announced"))
median_data <- solar_investment %>%
  filter(Estimated_Total_Facility_CAPEX > 0) %>%
  group_by(year, quarter) %>%
  summarise(median_investment_solar = median(Estimated_Total_Facility_CAPEX, na.rm = TRUE))
solar_investment <- solar_investment %>%
  left_join(median_data, by = c("year", "quarter"))
small_solar_investment <- solar_investment %>%
  filter(Estimated_Total_Facility_CAPEX <= median_investment_solar)
large_solar_investment <- solar_investment %>%
  filter(Estimated_Total_Facility_CAPEX > median_investment_solar)

small_solar_investment <- small_solar_investment %>%
  select(year, quarter, census_tract_2020_geoid, Estimated_Total_Facility_CAPEX) %>%
  group_by(census_tract_2020_geoid, year, quarter) %>%
  summarise(investment_small_solar = sum(Estimated_Total_Facility_CAPEX, na.rm = TRUE)) %>%
  ungroup() %>%
  rename("census_tract_id" = "census_tract_2020_geoid")

data <- left_join(data, small_solar_investment, by = c("census_tract_id", "year", "quarter"))
data$investment_small_solar <- ifelse(is.na(data$investment_small_solar), 0, 1)

large_solar_investment <- large_solar_investment %>%
  select(year, quarter, census_tract_2020_geoid, Estimated_Total_Facility_CAPEX) %>%
  group_by(census_tract_2020_geoid, year, quarter) %>%
  summarise(investment_large_solar = sum(Estimated_Total_Facility_CAPEX, na.rm = TRUE)) %>%
  ungroup() %>%
  rename("census_tract_id" = "census_tract_2020_geoid")

data <- left_join(data, large_solar_investment, by = c("census_tract_id", "year", "quarter"))
data$investment_large_solar <- ifelse(is.na(data$investment_large_solar), 0, 1)


wind_investment <- investment %>%
  filter(Technology == "Wind" & Segment == "Energy and Industry" & Current_Facility_Status %in% c("Under Construction", "Operating", "Announced"))
median_data <- wind_investment %>%
  filter(Estimated_Total_Facility_CAPEX > 0) %>%
  group_by(year, quarter) %>%
  summarise(median_investment_wind = median(Estimated_Total_Facility_CAPEX, na.rm = TRUE))
wind_investment <- wind_investment %>%
  left_join(median_data, by = c("year", "quarter"))
small_wind_investment <- wind_investment %>%
  filter(Estimated_Total_Facility_CAPEX <= median_investment_wind)
large_wind_investment <- wind_investment %>%
  filter(Estimated_Total_Facility_CAPEX > median_investment_wind)

small_wind_investment <- small_wind_investment %>%
  select(year, quarter, census_tract_2020_geoid, Estimated_Total_Facility_CAPEX) %>%
  group_by(census_tract_2020_geoid, year, quarter) %>%
  summarise(investment_small_wind = sum(Estimated_Total_Facility_CAPEX, na.rm = TRUE)) %>%
  ungroup() %>%
  rename("census_tract_id" = "census_tract_2020_geoid")

data <- left_join(data, small_wind_investment, by = c("census_tract_id", "year", "quarter"))
data$investment_small_wind <- ifelse(is.na(data$investment_small_wind), 0, 1)

large_wind_investment <- large_wind_investment %>%
  select(year, quarter, census_tract_2020_geoid, Estimated_Total_Facility_CAPEX) %>%
  group_by(census_tract_2020_geoid, year, quarter) %>%
  summarise(investment_large_wind = sum(Estimated_Total_Facility_CAPEX, na.rm = TRUE)) %>%
  ungroup() %>%
  rename("census_tract_id" = "census_tract_2020_geoid")

data <- left_join(data, large_wind_investment, by = c("census_tract_id", "year", "quarter"))
data$investment_large_wind <- ifelse(is.na(data$investment_large_wind), 0, 1)

rm(investment, large_solar_investment, large_wind_investment, median_data, small_solar_investment, small_wind_investment, solar_investment, wind_investment)
```

## Add a binary version 

```{r}
data$investment_solar_binary <- ifelse(data$investment_solar > 0, 1, 0)
data$investment_wind_binary <- ifelse(data$investment_wind > 0, 1, 0)
```

### Unemployment

```{r}
unemployment <- read.csv("Data/raw data/Unemployment2023.csv")
unemployment <- unemployment %>%
  filter(Attribute %in% c("Unemployment_rate_2000", "Unemployment_rate_2001", "Unemployment_rate_2002", "Unemployment_rate_2003", "Unemployment_rate_2004", "Unemployment_rate_2005", "Unemployment_rate_2006", "Unemployment_rate_2007", "Unemployment_rate_2008", "Unemployment_rate_2009", "Unemployment_rate_2010", "Unemployment_rate_2011", "Unemployment_rate_2012", "Unemployment_rate_2013", "Unemployment_rate_2014", "Unemployment_rate_2015", "Unemployment_rate_2016", "Unemployment_rate_2017", "Unemployment_rate_2018", "Unemployment_rate_2019", "Unemployment_rate_2020", "Unemployment_rate_2021", "Unemployment_rate_2022", "Unemployment_rate_2023")) 
unemployment$Attribute <- ifelse(unemployment$Attribute == "Unemployment_rate_2000", "2000", ifelse(unemployment$Attribute == "Unemployment_rate_2001", "2001", ifelse(unemployment$Attribute == "Unemployment_rate_2002", "2002", ifelse(unemployment$Attribute == "Unemployment_rate_2003", "2003", ifelse(unemployment$Attribute == "Unemployment_rate_2004", "2004", ifelse(unemployment$Attribute == "Unemployment_rate_2005", "2005", ifelse(unemployment$Attribute == "Unemployment_rate_2006", "2006", ifelse(unemployment$Attribute == "Unemployment_rate_2007", "2007", ifelse(unemployment$Attribute == "Unemployment_rate_2008", "2008", ifelse(unemployment$Attribute == "Unemployment_rate_2009", "2009", ifelse(unemployment$Attribute == "Unemployment_rate_2010", "2010", ifelse(unemployment$Attribute == "Unemployment_rate_2011", "2011", ifelse(unemployment$Attribute == "Unemployment_rate_2012", "2012", ifelse(unemployment$Attribute == "Unemployment_rate_2013", "2013", ifelse(unemployment$Attribute == "Unemployment_rate_2014", "2014", ifelse(unemployment$Attribute == "Unemployment_rate_2015", "2015", ifelse(unemployment$Attribute == "Unemployment_rate_2016", "2016", ifelse(unemployment$Attribute == "Unemployment_rate_2017", "2017", ifelse(unemployment$Attribute == "Unemployment_rate_2018", "2018", ifelse(unemployment$Attribute == "Unemployment_rate_2019", "2019", ifelse(unemployment$Attribute == "Unemployment_rate_2020", "2020", ifelse(unemployment$Attribute == "Unemployment_rate_2021", "2021", ifelse(unemployment$Attribute == "Unemployment_rate_2022", "2022", ifelse(unemployment$Attribute == "Unemployment_rate_2023", "2023", unemployment$Attribute))))))))))))))))))))))))
unemployment$Attribute <- as.numeric(unemployment$Attribute)
unemployment <- unemployment %>%
  select(FIPS_Code, Attribute, Value) %>%
  rename("county_id" = "FIPS_Code", "year" = "Attribute", "unemployment_rate" = "Value")
unemployment$county_id <- str_pad(unemployment$county_id, 5, pad = "0")

unemployment <- unemployment %>%
  bind_rows(
    distinct(unemployment, county_id) %>%
      mutate(year = 2024, unemployment_rate = NA_real_)
  ) %>%
  arrange(county_id, year)

unemployment <- unemployment %>%
  arrange(county_id, year) %>%
  group_by(county_id) %>%
  mutate(
    unemployment_lag1 = lag(unemployment_rate, 1),
    unemployment_lag2 = lag(unemployment_rate, 2),
    unemployment_lag3 = lag(unemployment_rate, 3),
    unemployment_lag4 = lag(unemployment_rate, 4)
  ) %>%
  ungroup()

# Step 2: Join onto your main dataset
data <- data %>%
  left_join(unemployment, by = c("county_id", "year"))

rm(unemployment)
```

## Filter and Save for use in Stata

```{r}
# Create treatment indicator
data$year_quarter <- paste0(data$year, "-", data$quarter)
data$treatment <- ifelse(data$year_quarter %in% c("2023-Q1", "2023-Q2", "2023-Q3", "2023-Q4", "2024-Q1") & data$ec_ind_official_cohort_1 == 1, 1, 0)
data$treatment <- ifelse(data$year_quarter %in% c("2024-Q2") & data$ec_ind_official_cohort_2 == 1, 1, data$treatment)
data$treatment <- ifelse(data$year_quarter %in% c("2024-Q3", "2024-Q4") & data$ec_ind_official_cohort_3 == 1, 1, data$treatment)

# Create period variable
data$year <- as.numeric(data$year)
base_year <- min(data$year)  # Using the minimum year in the dataset
data$quarter_num <- as.numeric(substr(data$quarter, 2, 2))
data$period <- (data$year - base_year) * 4 + data$quarter_num

data_stata <- data %>%
  st_drop_geometry() %>%
  select(census_tract_id, year, quarter, ec_ind_official_cohort_1, ec_ind_official_cohort_2, ec_ind_official_cohort_3, investment_small_solar, investment_large_solar, investment_small_wind, investment_large_wind, investment_solar, investment_wind, investment_solar_binary, investment_wind_binary, treatment, period, unemployment_rate, unemployment_lag1, unemployment_lag2, unemployment_lag2, unemployment_lag3, unemployment_lag4)
  
write.csv(data_stata, "Data/constructed data/investment_dataset_stata_with_unemployment.csv", row.names = FALSE)
```