---
title: "build_matching"
output: html_document
date: "2025-11-10"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Geographic regions

Here, we lay the groundwork by providing all the geographic regions in the dataset.

```{r}
# Add the census tracts
census_tracts <- sf::st_read("Data/raw data/tlgdb_2020_a_us_substategeo.gdb", layer = "Census_Tract")
census_tracts <- census_tracts %>%
  select("GEOID", "NAMELSAD", "SHAPE") %>%
  rename("census_tract_id" = "GEOID",
         "census_tract_name" = "NAMELSAD")
census_tracts$county_id <- str_sub(census_tracts$census_tract_id, 1, 5)
census_tracts$state_id <- str_sub(census_tracts$census_tract_id, 1, 2)
counties <- sf::st_read("Data/raw data/tlgdb_2020_a_us_substategeo.gdb", layer = "County")
counties <- counties %>%
  select("GEOID", "NAMELSAD") %>%
  rename("county_id" = "GEOID",
         "county_name" = "NAMELSAD") %>%
  st_drop_geometry()
census_tracts <- left_join(census_tracts, counties, by = "county_id")

rm(counties)
```

## Add the 2023 (cohort 1) energy communities: IRS notice 2023-29

```{r}
coal_closure <- read.csv("Data/raw data/IRA_Coal_Closure_Energy_Comm_2023v2/Coal_Closure_Energy_Communities_2023v2.csv")
coal_closure$geoid_tract_2020 <- str_pad(coal_closure$geoid_tract_2020, 11, pad = "0")
EC_employ <- read.csv("Data/raw data/MSA_NMSA_FEE_EC_Status_2023v2/MSA_NMSA_FFE_EC_2023v2.csv")
EC_employ$geoid_cty_2020 <- str_pad(EC_employ$geoid_cty_2020, 5, pad = "0")
coal_closure_mine <- coal_closure %>%
  filter(Tract_Status %in% c("is an energy community due to a coal mine closure"))
coal_closure_mine <- unique(coal_closure_mine$geoid_tract_2020)
coal_closure_generator <- coal_closure %>%
  filter(Generator_Closure == "Yes")
coal_closure_generator <- unique(coal_closure_generator$geoid_tract_2020)
coal_closure_adjacent <- coal_closure %>%
  filter(Adjacent_to_Closure == "Yes")
coal_closure_adjacent <- unique(coal_closure_adjacent$geoid_tract_2020)
EC_employ <- unique(EC_employ[EC_employ$EC_qual_status == "Yes", ]$geoid_cty_2020)

data <- census_tracts

data$coal_mine_closure_official_cohort_1 <- ifelse(data$census_tract_id %in% coal_closure_mine, 1, 0)
data$generator_closure_official_cohort_1 <- ifelse(data$census_tract_id %in% coal_closure_generator, 1, 0)
data$adjacent_closure_official_cohort_1 <- ifelse(data$census_tract_id %in% coal_closure_adjacent, 1, 0)
data$unemployment_official_msa_cohort_1 <- ifelse(data$county_id %in% EC_employ, 1, 0)

rm(coal_closure, EC_employ, coal_closure_adjacent, coal_closure_generator, coal_closure_mine)
```

## Add the 2023 (cohort 2) energy communities: IRS notice 2024-30

```{r}
coal_closure <- read.csv("Data/raw data/IRA_Coal_Closure_Energy_Comm_2023v2/Coal_Closure_Energy_Communities_2023v2.csv")
coal_closure$geoid_tract_2020 <- str_pad(coal_closure$geoid_tract_2020, 11, pad = "0")
EC_employ <- read.csv("Data/raw data/MSA_NMSA_EC_FFE_Status_v2023_3/MSA_NonMSA_EnergyCommunities_FossilFuelEmp_2023v3.csv")
EC_employ$geoid_county_2020 <- str_pad(EC_employ$geoid_county_2020, 5, pad = "0")
coal_closure_mine <- coal_closure %>%
  filter(Tract_Status %in% c("is an energy community due to a coal mine closure"))
coal_closure_mine <- unique(coal_closure_mine$geoid_tract_2020)
coal_closure_generator <- coal_closure %>%
  filter(Generator_Closure == "Yes")
coal_closure_generator <- unique(coal_closure_generator$geoid_tract_2020)
coal_closure_adjacent <- coal_closure %>%
  filter(Adjacent_to_Closure == "Yes")
coal_closure_adjacent <- unique(coal_closure_adjacent$geoid_tract_2020)
EC_employ <- unique(EC_employ[EC_employ$ec_qual_status == "Yes", ]$geoid_county_2020)

data$coal_mine_closure_official_cohort_2 <- ifelse(data$census_tract_id %in% coal_closure_mine, 1, 0)
data$generator_closure_official_cohort_2 <- ifelse(data$census_tract_id %in% coal_closure_generator, 1, 0)
data$adjacent_closure_official_cohort_2 <- ifelse(data$census_tract_id %in% coal_closure_adjacent, 1, 0)
data$unemployment_official_msa_cohort_2 <- ifelse(data$county_id %in% EC_employ, 1, 0)

rm(coal_closure, EC_employ, coal_closure_adjacent, coal_closure_generator, coal_closure_mine)
```

## Add the 2024 (cohort 3) energy communities: IRS notice 2024-48

```{r}
coal_closure <- read.csv("Data/raw data/Coal_Closures_EnergyComm_v2024_1/IRA_EnergyComm_CTracts_CoalClosures_v2024_1.csv")
coal_closure$geoid_tract_2020 <- str_pad(coal_closure$geoid_tract_2020, 11, pad = "0")
EC_employ <- read.csv("Data/raw data/MSA_NMSA_EC_FFE_v2024_1/MSA_NonMSA_EnergyCommunities_FossilFuelEmp_v2024_1.csv")
EC_employ$geoid_county_2020 <- str_pad(EC_employ$geoid_county_2020, 5, pad = "0")
coal_closure_mine <- coal_closure %>%
  filter(Mine_Closure == "Yes")
coal_closure_mine <- unique(coal_closure_mine$geoid_tract_2020)
coal_closure_generator <- coal_closure %>%
  filter(Generator_Closure == "Yes")
coal_closure_generator <- unique(coal_closure_generator$geoid_tract_2020)
coal_closure_adjacent <- coal_closure %>%
  filter(Adjacent_to_Closure == "Yes")
coal_closure_adjacent <- unique(coal_closure_adjacent$geoid_tract_2020)
EC_employ <- unique(EC_employ[EC_employ$ec_qual_status == "Yes", ]$geoid_county_2020)

data$coal_mine_closure_official_cohort_3 <- ifelse(data$census_tract_id %in% coal_closure_mine, 1, 0)
data$generator_closure_official_cohort_3 <- ifelse(data$census_tract_id %in% coal_closure_generator, 1, 0)
data$adjacent_closure_official_cohort_3 <- ifelse(data$census_tract_id %in% coal_closure_adjacent, 1, 0)
data$unemployment_official_msa_cohort_3 <- ifelse(data$county_id %in% EC_employ, 1, 0)

rm(coal_closure, EC_employ, coal_closure_adjacent, coal_closure_generator, coal_closure_mine)
```

## Add binary indicator for energy communities

```{r}
data <- data %>%
  mutate(ec_ind_official_cohort_1 = ifelse((coal_mine_closure_official_cohort_1 == 1 | 
                                   generator_closure_official_cohort_1 == 1 | 
                                   adjacent_closure_official_cohort_1 == 1) |
                                   unemployment_official_msa_cohort_1 == 1, 
                                   1, 0))

data <- data %>%
  mutate(ec_ind_official_cohort_2 = ifelse((coal_mine_closure_official_cohort_2 == 1 | 
                                   generator_closure_official_cohort_2 == 1 | 
                                   adjacent_closure_official_cohort_2 == 1) |
                                   unemployment_official_msa_cohort_2 == 1, 
                                   1, 0))

data <- data %>%
  mutate(ec_ind_official_cohort_3 = ifelse((coal_mine_closure_official_cohort_3 == 1 | 
                                   generator_closure_official_cohort_3 == 1 | 
                                   adjacent_closure_official_cohort_3 == 1) |
                                   unemployment_official_msa_cohort_3 == 1, 
                                   1, 0))

data$ec_ind_official <- ifelse(data$ec_ind_official_cohort_1 == 1 | data$ec_ind_official_cohort_2 == 1 | data$ec_ind_official_cohort_3 == 1, 1, 0)
```

## For weights we add variables which determine the likelihood of investment and employment

### Surface Area

```{r}
## Land Surface Area
data <- st_as_sf(data)
data$area <- st_area(data)/1000
```

### Demographic variables

```{r}
population <- read.csv("Data/raw data/DECENNIALDP2020.DP1_2024-04-08T040530/DECENNIALDP2020.DP1-Data.csv")
population <- population[-1, ]
population <- subset(population, select = c("GEO_ID", "NAME", "DP1_0001C"))
population <- population %>%
  rename("total_population_2020" = "DP1_0001C")
population$census_tract_id <- sub(".*US", "", population$GEO_ID)
population <- population %>%
  select(-c("GEO_ID", "NAME"))

population$total_population_2020 <- as.numeric(population$total_population_2020)

# Merge the demographics with the complete dataset
data <- left_join(data, population, by = "census_tract_id")

rm(population)
```

### Energy Generating Potential

```{r}
# Read in and prepare the energy generating potential dataset
energy <- read.csv("Data/raw data/66600e58b2ec97558133d632_results.csv")
fips <- read_excel("Data/raw data/usa_adm2_geoquery_fips.xlsx")
energy <- left_join(energy, fips, by = "shapeID")
energy <- energy %>%
  select("globalsolaratlas_pvout.none.mean", "globalsolaratlas_pvout.none.max", "globalsolaratlas_pvout.none.min", "globalwindatlas_windspeed.none.mean", "globalwindatlas_windspeed.none.max", "globalwindatlas_windspeed.none.min", "globalwindatlas_powerdensity.none.mean", "globalwindatlas_powerdensity.none.max", "globalwindatlas_powerdensity.none.min", "GEOID") %>%
  rename("mean_solar_potential_county_2019" = "globalsolaratlas_pvout.none.mean", "max_solar_potential_county_2019" = "globalsolaratlas_pvout.none.max", "min_solar_potential_county_2019" = "globalsolaratlas_pvout.none.min", "mean_wind_potential_county_2019" = "globalwindatlas_windspeed.none.mean", "max_wind_potential_county_2019" = "globalwindatlas_windspeed.none.max", "min_wind_potential_county_2019" = "globalwindatlas_windspeed.none.min", "mean_wind_density_potential_county_2019" = "globalwindatlas_powerdensity.none.mean", "max_wind_density_potential_county_2019" = "globalwindatlas_powerdensity.none.max", "min_wind_density_potential_county_2019" = "globalwindatlas_powerdensity.none.min", "county_id" = "GEOID")
energy$county_id <- str_pad(energy$county_id, 5, pad = "0")

data <- left_join(data, energy, by = "county_id")
```

### Educational attainment

```{r}
education <- read_excel("Data/raw data/Educational Attainment 2018-2022_-7235352158010358632.xlsx")

education <- education %>%
  select("GEOID", "Population 25 years and over - 9th to 12th grade, no diploma (%)", "Population 25 years and over - High school graduate (includes equivalency) (%)", "Population 25 years and over - Associate's degree (%)", "Population 25 years and over - Bachelor's degree or higher (%)") %>%
  rename("county_id" = "GEOID", "percentage_no_high_school_county_18_22" = "Population 25 years and over - 9th to 12th grade, no diploma (%)", "percentage_high_school_county_18_22" = "Population 25 years and over - High school graduate (includes equivalency) (%)", "percentage_college_county_18_22" = "Population 25 years and over - Associate's degree (%)", "percentage_bachelor_county_18_22" = "Population 25 years and over - Bachelor's degree or higher (%)")

# Merge the datasets
data <- left_join(data, education, by = "county_id")

rm(education)
```

### Industry GDP

```{r}
gdp <- read.csv("Data/raw data/CAGDP9__ALL_AREAS_2017_2022.csv")

gdp <- gdp %>%
  rename("Industry" = "Description") %>%
  rename_with(~ str_remove(., "^X"), starts_with("X20")) %>%  # strip the X prefix from year columns
  select("GeoFIPS", "Industry", "2018", "2019", "2020", "2021", "2022") %>%
  pivot_longer(cols = starts_with("20"), names_to = "year", values_to = "Value")

gdp$Industry <- str_trim(gdp$Industry)

gdp <- gdp %>%
  filter(Industry %in% c("All industry total", "Government and government enterprises", 
                          "Natural resources and mining", "Trade", 
                          "Transportation and utilities", "Manufacturing and information")) %>%
  mutate(
    Industry = recode(Industry,
      "Trade"                                  = "trade",
      "Transportation and utilities"           = "transportation_utilities",
      "Government and government enterprises"  = "government",
      "All industry total"                     = "all_industry_total",
      "Manufacturing and information"          = "manufacturing_information",
      "Natural resources and mining"           = "natural_resources_mining"
    ),
    col_name = paste0(Industry, "_gdp_county_", year)
  ) %>%
  select(-Industry, -year) %>%
  pivot_wider(names_from = col_name, values_from = Value)

gdp <- gdp %>%
  rename("county_id" = "GeoFIPS")

gdp$county_id <- str_trim(gdp$county_id)

# Convert all GDP columns to numeric
gdp <- gdp %>%
  mutate(across(-county_id, ~ as.numeric(str_trim(.))))

# Add to the complete dataset
data <- left_join(data, gdp, by = "county_id")
rm(gdp)
```

## Include generators of 2022, Q2

```{r}
# Add the census tracts
census_tracts <- sf::st_read("Data/raw data/tlgdb_2020_a_us_substategeo.gdb", layer = "Census_Tract")

# Read generator data
generators <- read_excel("Data/raw data/eia_monthly_data/april_generator2022.xlsx") %>%
  setNames(.[2, ]) %>%        # Set first row as column names
  slice(-1) %>% 
  slice(-1) %>% 
  filter(!is.na(Latitude), !is.na(Longitude)) %>%  # Filter rows with valid Latitude and Longitude
  st_as_sf(coords = c("Longitude", "Latitude"), crs = 4326) %>%
  st_transform(crs = st_crs(census_tracts)) %>%
  filter(Sector == "Electric Utility") %>%
  filter(Status == "(OP) Operating")

# Find generators within census tracts and assign corresponding row numbers
generators$census_tract_row_number <- st_within(generators, census_tracts) %>% as.numeric()

# Process generator data: summarize capacities by technology and reshape
names(generators) <- gsub("^\\s+|\\s+$", "", names(generators))
generators <- generators %>%
  st_drop_geometry() %>%
  select(nameplate_capacity = `Net Summer Capacity (MW)`, Technology, census_tract_row_number) %>%
  mutate(nameplate_capacity = as.numeric(nameplate_capacity)) %>%
  group_by(census_tract_row_number, Technology) %>%
  summarize(nameplate_capacity = sum(nameplate_capacity, na.rm = TRUE), .groups = "drop") %>%
  pivot_wider(names_from = Technology, values_from = nameplate_capacity, values_fill = 0) %>%
  mutate(
    total_MW_2022_Q2 = rowSums(select(., -c(census_tract_row_number)), na.rm = TRUE),
    hydro_MW_2022_Q2 = `Conventional Hydroelectric` + `Hydroelectric Pumped Storage`,
    natural_gas_MW_2022_Q2 = `Natural Gas Fired Combined Cycle` + `Natural Gas Steam Turbine` +
                     `Natural Gas Fired Combustion Turbine` + `Natural Gas Internal Combustion Engine` + `Natural Gas with Compressed Air Storage`,
    coal_MW_2022_Q2 = `Conventional Steam Coal` + `Coal Integrated Gasification Combined Cycle`,
    other_fossil_MW_2022_Q2 = `Petroleum Liquids` + `Landfill Gas` + `Petroleum Coke`,
    solar_MW_2022_Q2 = `Solar Photovoltaic`,
    onshore_wind_MW_2022_Q2 = `Onshore Wind Turbine`,
    nuclear_MW_2022_Q2 = Nuclear
  ) %>%
  select(census_tract_row_number, total_MW_2022_Q2, hydro_MW_2022_Q2, natural_gas_MW_2022_Q2, coal_MW_2022_Q2, other_fossil_MW_2022_Q2, solar_MW_2022_Q2, onshore_wind_MW_2022_Q2, nuclear_MW_2022_Q2)

# Add census tract ID to generators
generators <- generators %>%
  mutate(census_tract_id = census_tracts$GEOID[census_tract_row_number]) %>%
  select(-census_tract_row_number)

# Merge final data with generators on census tract ID, year, and quarter
data <- left_join(data, generators, by = "census_tract_id")
```

### rural urban continuum code and urban influence code

```{r}
poverty <- read.csv("Data/raw data/Poverty2023.csv")
poverty <- poverty %>%
  filter(Attribute %in% c("Rural_Urban_Continuum_Code_2013", "Urban_Influence_Code_2013")) %>%
  pivot_wider(id_cols = FIPS_Code, names_from = Attribute, values_from = Value) %>%
  rename("county_id" = "FIPS_Code", "rural_urban_continuum_code_2013" = "Rural_Urban_Continuum_Code_2013", "urban_influence_code_2013" = "Urban_Influence_Code_2013")
poverty$county_id <- str_pad(poverty$county_id, 5, pad = "0")

# Merge the datasets
data <- left_join(data, poverty, by = "county_id")

rm(poverty)
```

### Unemployment

```{r}
unemployment <- read.csv("Data/raw data/Unemployment2023.csv")
unemployment <- unemployment %>%
  filter(Attribute %in% c("Unemployment_rate_2022", "Unemployment_rate_2021", "Unemployment_rate_2020", "Unemployment_rate_2019", "Unemployment_rate_2018")) %>%
  pivot_wider(id_cols = FIPS_Code, names_from = Attribute, values_from = Value) %>%
  rename("county_id" = "FIPS_Code", "unemployment_rate_2022" = "Unemployment_rate_2022", "unemployment_rate_2021" = "Unemployment_rate_2021", "unemployment_rate_2020" = "Unemployment_rate_2020", "unemployment_rate_2019" = "Unemployment_rate_2019", "unemployment_rate_2018" = "Unemployment_rate_2018")
unemployment$county_id <- str_pad(unemployment$county_id, 5, pad = "0")

# Merge unemployment to the complete dataset
data <- left_join(data, unemployment, by = c("county_id"))

rm(unemployment)
```

## Change some variables 

```{r}
data$area <- as.numeric(data$area)
data$solar_MW_2022_Q2 <- ifelse(is.na(data$solar_MW_2022_Q2), 0, data$solar_MW_2022_Q2)
data$onshore_wind_MW_2022_Q2 <- ifelse(is.na(data$onshore_wind_MW_2022_Q2), 0, data$onshore_wind_MW_2022_Q2)
data$nuclear_MW_2022_Q2 <- ifelse(is.na(data$nuclear_MW_2022_Q2), 0, data$nuclear_MW_2022_Q2)
data$natural_gas_MW_2022_Q2 <- ifelse(is.na(data$natural_gas_MW_2022_Q2), 0, data$natural_gas_MW_2022_Q2)
data$total_MW_2022_Q2 <- ifelse(is.na(data$total_MW_2022_Q2), 0, data$total_MW_2022_Q2)
data$hydro_MW_2022_Q2 <- ifelse(is.na(data$hydro_MW_2022_Q2), 0, data$hydro_MW_2022_Q2)
data$coal_MW_2022_Q2 <- ifelse(is.na(data$coal_MW_2022_Q2), 0, data$coal_MW_2022_Q2)
data$other_fossil_MW_2022_Q2 <- ifelse(is.na(data$other_fossil_MW_2022_Q2), 0, data$other_fossil_MW_2022_Q2)
# GDP variables - replace all NAs with 0 across all years
data <- data %>%
  mutate(across(
    starts_with(c("government_gdp_county_",
                  "natural_resources_mining_gdp_county_",
                  "trade_gdp_county_",
                  "transportation_utilities_gdp_county_",
                  "manufacturing_information_gdp_county_",
                  "all_industry_total_gdp_county_")),
    ~ ifelse(is.na(.), 0, .)
  ))

data_census_tract <- data %>%
  st_drop_geometry() %>%
  select("census_tract_id", "state_id", "ec_ind_official", "area", "total_population_2020", 
         "mean_solar_potential_county_2019", "max_solar_potential_county_2019", 
         "min_solar_potential_county_2019", "mean_wind_potential_county_2019", 
         "max_wind_potential_county_2019", "min_wind_potential_county_2019", 
         "mean_wind_density_potential_county_2019", "max_wind_density_potential_county_2019", 
         "min_wind_density_potential_county_2019", "percentage_no_high_school_county_18_22", 
         "percentage_high_school_county_18_22", "percentage_college_county_18_22", 
         "percentage_bachelor_county_18_22", "urban_influence_code_2013", 
         "rural_urban_continuum_code_2013",
         starts_with("all_industry_total_gdp_county_"),
         starts_with("government_gdp_county_"),
         starts_with("natural_resources_mining_gdp_county_"),
         starts_with("trade_gdp_county_"),
         starts_with("transportation_utilities_gdp_county_"),
         starts_with("manufacturing_information_gdp_county_"),
         "total_MW_2022_Q2", "hydro_MW_2022_Q2", "natural_gas_MW_2022_Q2", "coal_MW_2022_Q2", 
         "other_fossil_MW_2022_Q2", "solar_MW_2022_Q2", "onshore_wind_MW_2022_Q2", 
         "nuclear_MW_2022_Q2", 
         starts_with("unemployment_rate_")) %>%
  ungroup() %>%
  drop_na(mean_solar_potential_county_2019, max_solar_potential_county_2019, 
          min_solar_potential_county_2019, mean_wind_potential_county_2019,
          max_wind_potential_county_2019, min_wind_potential_county_2019, 
          mean_wind_density_potential_county_2019, max_wind_density_potential_county_2019, 
          min_wind_density_potential_county_2019, percentage_no_high_school_county_18_22,
          percentage_high_school_county_18_22, percentage_college_county_18_22, 
          percentage_bachelor_county_18_22, urban_influence_code_2013,
          rural_urban_continuum_code_2013, all_industry_total_gdp_county_2022, 
          unemployment_rate_2022, unemployment_rate_2021, unemployment_rate_2020, 
          unemployment_rate_2019, unemployment_rate_2018) %>%
  filter(if_all(starts_with(c("all_industry_total_gdp_county_",
                               "government_gdp_county_",
                               "natural_resources_mining_gdp_county_",
                               "trade_gdp_county_",
                               "transportation_utilities_gdp_county_",
                               "manufacturing_information_gdp_county_")), 
                ~ !is.na(.)))

data_county <- data %>%
  st_drop_geometry() %>%
  select("county_id", "state_id", "ec_ind_official", "area", "total_population_2020", 
         "mean_solar_potential_county_2019", "max_solar_potential_county_2019", 
         "min_solar_potential_county_2019", "mean_wind_potential_county_2019", 
         "max_wind_potential_county_2019", "min_wind_potential_county_2019", 
         "mean_wind_density_potential_county_2019", "max_wind_density_potential_county_2019", 
         "min_wind_density_potential_county_2019", "percentage_no_high_school_county_18_22", 
         "percentage_high_school_county_18_22", "percentage_college_county_18_22", 
         "percentage_bachelor_county_18_22", "urban_influence_code_2013", 
         "rural_urban_continuum_code_2013",
         starts_with("unemployment_rate_"),
         starts_with("all_industry_total_gdp_county_"),
         starts_with("government_gdp_county_"),
         starts_with("natural_resources_mining_gdp_county_"),
         starts_with("trade_gdp_county_"),
         starts_with("transportation_utilities_gdp_county_"),
         starts_with("manufacturing_information_gdp_county_"),
         "total_MW_2022_Q2", "hydro_MW_2022_Q2", "natural_gas_MW_2022_Q2", "coal_MW_2022_Q2", 
         "other_fossil_MW_2022_Q2", "solar_MW_2022_Q2", "onshore_wind_MW_2022_Q2", 
         "nuclear_MW_2022_Q2") %>%
  group_by(county_id) %>%
  summarise(
    state_id = first(state_id),
    ec_ind_official = max(ec_ind_official, na.rm = TRUE),
    mean_solar_potential_county_2019 = first(mean_solar_potential_county_2019),
    max_solar_potential_county_2019 = first(max_solar_potential_county_2019),
    min_solar_potential_county_2019 = first(min_solar_potential_county_2019),
    mean_wind_potential_county_2019 = first(mean_wind_potential_county_2019),
    max_wind_potential_county_2019 = first(max_wind_potential_county_2019),
    min_wind_potential_county_2019 = first(min_wind_potential_county_2019),
    mean_wind_density_potential_county_2019 = first(mean_wind_density_potential_county_2019),
    max_wind_density_potential_county_2019 = first(max_wind_density_potential_county_2019),
    min_wind_density_potential_county_2019 = first(min_wind_density_potential_county_2019),
    percentage_no_high_school_county_18_22 = first(percentage_no_high_school_county_18_22),
    percentage_high_school_county_18_22 = first(percentage_high_school_county_18_22),
    percentage_college_county_18_22 = first(percentage_college_county_18_22),
    percentage_bachelor_county_18_22 = first(percentage_bachelor_county_18_22),
    urban_influence_code_2013 = first(urban_influence_code_2013),
    rural_urban_continuum_code_2013 = first(rural_urban_continuum_code_2013),
    across(starts_with(c("all_industry_total_gdp_county_",
                          "government_gdp_county_",
                          "natural_resources_mining_gdp_county_",
                          "trade_gdp_county_",
                          "transportation_utilities_gdp_county_",
                          "manufacturing_information_gdp_county_",
                         "unemployment_rate_")),
           first),
    area = sum(area, na.rm = TRUE),
    total_population_2020 = sum(total_population_2020, na.rm = TRUE),
    total_MW_2022_Q2 = sum(total_MW_2022_Q2, na.rm = TRUE),
    hydro_MW_2022_Q2 = sum(hydro_MW_2022_Q2, na.rm = TRUE),
    natural_gas_MW_2022_Q2 = sum(natural_gas_MW_2022_Q2, na.rm = TRUE),
    coal_MW_2022_Q2 = sum(coal_MW_2022_Q2, na.rm = TRUE),
    other_fossil_MW_2022_Q2 = sum(other_fossil_MW_2022_Q2, na.rm = TRUE),
    solar_MW_2022_Q2 = sum(solar_MW_2022_Q2, na.rm = TRUE),
    onshore_wind_MW_2022_Q2 = sum(onshore_wind_MW_2022_Q2, na.rm = TRUE),
    nuclear_MW_2022_Q2 = sum(nuclear_MW_2022_Q2, na.rm = TRUE)
  ) %>%
  ungroup() %>%
  drop_na(mean_solar_potential_county_2019, max_solar_potential_county_2019, 
          min_solar_potential_county_2019, mean_wind_potential_county_2019,
          max_wind_potential_county_2019, min_wind_potential_county_2019, 
          mean_wind_density_potential_county_2019, max_wind_density_potential_county_2019, 
          min_wind_density_potential_county_2019, percentage_no_high_school_county_18_22,
          percentage_high_school_county_18_22, percentage_college_county_18_22, 
          percentage_bachelor_county_18_22, urban_influence_code_2013,
          rural_urban_continuum_code_2013, all_industry_total_gdp_county_2022) %>%
  filter(if_all(starts_with(c("all_industry_total_gdp_county_",
                               "government_gdp_county_",
                               "natural_resources_mining_gdp_county_",
                               "trade_gdp_county_",
                               "transportation_utilities_gdp_county_",
                               "manufacturing_information_gdp_county_",
                              "unemployment_rate_")), 
                ~ !is.na(.)))
```

## Matching on LASSO selected variables

# Create matches for investment

```{r}
# All Variables
matching_vars <- c(
   "all_industry_total_gdp_county_2022", "government_gdp_county_2022", "natural_resources_mining_gdp_county_2022", "trade_gdp_county_2022", "transportation_utilities_gdp_county_2022", "manufacturing_information_gdp_county_2022", "unemployment_rate_2022")

matching_vars <- c("area", "total_population_2020", "mean_solar_potential_county_2019", "max_solar_potential_county_2019", "min_solar_potential_county_2019", "mean_wind_potential_county_2019", "max_wind_potential_county_2019", "min_wind_potential_county_2019", "mean_wind_density_potential_county_2019", "max_wind_density_potential_county_2019", "min_wind_density_potential_county_2019", "percentage_no_high_school_county_18_22", "percentage_high_school_county_18_22", "percentage_college_county_18_22", "percentage_bachelor_county_18_22", "urban_influence_code_2013", "rural_urban_continuum_code_2013", "unemployment_rate_2018", "unemployment_rate_2019", "unemployment_rate_2020", "unemployment_rate_2021", "unemployment_rate_2022", "all_industry_total_gdp_county_2018", "all_industry_total_gdp_county_2019", "all_industry_total_gdp_county_2020", "all_industry_total_gdp_county_2021", "all_industry_total_gdp_county_2022", "government_gdp_county_2018", "government_gdp_county_2019", "government_gdp_county_2020", "government_gdp_county_2021", "government_gdp_county_2022", "natural_resources_mining_gdp_county_2018", "natural_resources_mining_gdp_county_2019", "natural_resources_mining_gdp_county_2020", "natural_resources_mining_gdp_county_2021", "natural_resources_mining_gdp_county_2022",  "trade_gdp_county_2018", "trade_gdp_county_2019", "trade_gdp_county_2020", "trade_gdp_county_2021", "trade_gdp_county_2022", "transportation_utilities_gdp_county_2018", "transportation_utilities_gdp_county_2019", "transportation_utilities_gdp_county_2020",  "transportation_utilities_gdp_county_2021", "transportation_utilities_gdp_county_2022", "manufacturing_information_gdp_county_2018", "manufacturing_information_gdp_county_2019", "manufacturing_information_gdp_county_2020", "manufacturing_information_gdp_county_2021", "manufacturing_information_gdp_county_2022", "total_MW_2022_Q2", "hydro_MW_2022_Q2", "natural_gas_MW_2022_Q2", "coal_MW_2022_Q2", "other_fossil_MW_2022_Q2", "solar_MW_2022_Q2", "onshore_wind_MW_2022_Q2", "nuclear_MW_2022_Q2")

# Step 2: Run LASSO for variable selection
# Prepare matrix of predictors
X <- data_census_tract %>%
  select(all_of(matching_vars)) %>%
  as.matrix()

# Remove rows with any NAs
complete_rows <- complete.cases(X, data_census_tract$ec_ind_official)
X <- X[complete_rows, ]
y <- data_census_tract$ec_ind_official[complete_rows]

# Standardize predictors for LASSO
X_scaled <- scale(X)

# Run LASSO with cross-validation
set.seed(123)  # For reproducibility
cv_lasso <- cv.glmnet(X_scaled, y, 
                       family = "binomial",
                       alpha = 1,  # 1 = LASSO, 0 = Ridge
                       nfolds = 10)

# Plot cross-validation results
plot(cv_lasso)

# Step 3: Select variables based on LASSO
lasso_coef <- coef(cv_lasso, s = "lambda.1se")

# Extract non-zero coefficients (selected variables)
selected_vars <- rownames(lasso_coef)[which(lasso_coef != 0)]
selected_vars <- selected_vars[selected_vars != "(Intercept)"]  # Remove intercept

print(paste("LASSO selected", length(selected_vars), "variables:"))
print(selected_vars)

# Create a coefficient plot
lasso_coef_df <- as.data.frame(as.matrix(lasso_coef))
lasso_coef_df$variable <- rownames(lasso_coef_df)
names(lasso_coef_df)[1] <- "coefficient"

lasso_coef_df %>%
  mutate(variable = recode(variable,
                           "area" = "Area",
                           "total_population_2020" = "Total Population",
                           "mean_solar_potential_county_2019" = "Mean Solar Energy Generating Potential",
                           "max_solar_potential_county_2019" = "Max Solar Energy Generating Potential",
                           "min_solar_potential_county_2019" = "Min Solar Energy Generating Potential",
                           "mean_wind_potential_county_2019" = "Mean Wind Energy Generating Potential",
                           "max_wind_potential_county_2019" = "Max Wind Energy Generating Potential",
                           "min_wind_potential_county_2019" = "Min Wind Energy Generating Potential",
                           "mean_wind_density_potential_county_2019" = "Mean Wind Energy Density Potential",
                           "max_wind_density_potential_county_2019" = "Max Wind Energy Density Potential",
                           "min_wind_density_potential_county_2019" = "Min Wind Energy Density Potential",
                           "percentage_no_high_school_county_18_22" = "Education: No High School",
                           "percentage_high_school_county_18_22" = "Education: High School Graduates",
                           "percentage_college_county_18_22" = "Education: College Graduates",
                           "percentage_bachelor_county_18_22" = "Education: Bachelor Graduates",
                           "urban_influence_code_2013" = "Urban Influence Code",
                           "rural_urban_continuum_code_2013" = "Rural Urban Continuum Code",
                           "total_MW_2022_Q2" = "Total Energy Generation",
                           "hydro_MW_2022_Q2" = "Hydro Energy Generation",
                           "natural_gas_MW_2022_Q2" = "Natural Gas Energy Generation",
                           "coal_MW_2022_Q2" = "Coal Energy Generation",
                           "other_fossil_MW_2022_Q2" = "Other Fossil Energy Generation",
                           "solar_MW_2022_Q2" = "Solar Energy Generation",
                           "onshore_wind_MW_2022_Q2" = "Onshore Wind Energy Generation",
                           "nuclear_MW_2022_Q2" = "Nuclear Energy Generation",
                           "unemployment_rate_2022" = "Unemployment Rate 2022",
                           "unemployment_rate_2021" = "Unemployment Rate 2021",
                           "unemployment_rate_2020" = "Unemployment Rate 2020",
                           "unemployment_rate_2019" = "Unemployment Rate 2019",
                           "unemployment_rate_2018" = "Unemployment Rate 2018",
                           "all_industry_total_gdp_county_2018" = "Total GDP 2018", 
                           "all_industry_total_gdp_county_2019" = "Total GDP 2019", 
                           "all_industry_total_gdp_county_2020" = "Total GDP 2020", 
                           "all_industry_total_gdp_county_2021" = "Total GDP 2021", 
                           "all_industry_total_gdp_county_2022" = "Total GDP 2022", 
                           "government_gdp_county_2018" = "Government GDP 2018",
                           "government_gdp_county_2019" = "Government GDP 2019",
                           "government_gdp_county_2020" = "Government GDP 2020",
                           "government_gdp_county_2021" = "Government GDP 2021",
                           "government_gdp_county_2022" = "Government GDP 2022",
                           "natural_resources_mining_gdp_county_2018" = "Natural Resources Mining GDP 2018",
                           "natural_resources_mining_gdp_county_2019" = "Natural Resources Mining GDP 2019",
                           "natural_resources_mining_gdp_county_2020" = "Natural Resources Mining GDP 2020",
                           "natural_resources_mining_gdp_county_2021" = "Natural Resources Mining GDP 2021",
                           "natural_resources_mining_gdp_county_2022" = "Natural Resources Mining GDP 2022",
                           "trade_gdp_county_2018" = "Trade GDP 2018", 
                           "trade_gdp_county_2019" = "Trade GDP 2019", 
                           "trade_gdp_county_2020" = "Trade GDP 2020", 
                           "trade_gdp_county_2021" = "Trade GDP 2021", 
                           "trade_gdp_county_2022" = "Trade GDP 2022", 
                           "transportation_utilities_gdp_county_2018" = "Transportation & Utilities GDP 2018",
                           "transportation_utilities_gdp_county_2019" = "Transportation & Utilities GDP 2019",
                           "transportation_utilities_gdp_county_2020" = "Transportation & Utilities GDP 2020", 
                           "transportation_utilities_gdp_county_2021" = "Transportation & Utilities GDP 2021", 
                           "transportation_utilities_gdp_county_2022" = "Transportation & Utilities GDP 2022",
                           "manufacturing_information_gdp_county_2018" = "Manufacturing & Information GDP 2018", 
                           "manufacturing_information_gdp_county_2019" = "Manufacturing & Information GDP 2019", 
                           "manufacturing_information_gdp_county_2020" = "Manufacturing & Information GDP 2020", 
                           "manufacturing_information_gdp_county_2021" = "Manufacturing & Information GDP 2021", 
                           "manufacturing_information_gdp_county_2022" = "Manufacturing & Information GDP 2022")) %>%
  filter(variable != "(Intercept)" & coefficient != 0) %>%
  ggplot(aes(x = reorder(variable, abs(coefficient)), y = coefficient)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  coord_flip() +
  labs(x = "Variable", y = "LASSO Coefficient") +
  theme_minimal()
ggsave("Output/lasso_coefficients_investment_all_variables.png", width = 8, height = 6)

# Step 4: Alternative - show coefficients across lambda values
lasso_full <- glmnet(X_scaled, y, family = "binomial", alpha = 1)
plot(lasso_full, xvar = "lambda", label = TRUE)

# Step 5: Run matching with LASSO-selected variables
# Create formula with selected variables
match_formula <- as.formula(paste("ec_ind_official ~", 
                                  paste(selected_vars, collapse = " + ")))

# Perform matching
match_out <- matchit(
  match_formula,
  data = data_census_tract[complete_rows, ],  # Use same subset as LASSO
  method = "nearest",
  distance = "logit",
  replace = FALSE,
  caliper = 0.1,
  ratio = 1
)

love_plot <- love.plot(
  match_out,
  thresholds = c(m = 0.1),
  abs = TRUE,
  colors = c("red", "blue"),
  shapes = c(19, 17),
  title = NULL,
  # Provide a named vector of old names -> new labels
  var.names = c(
                           "area" = "Area",
                           "total_population_2020" = "Total Population",
                           "mean_solar_potential_county_2019" = "Mean Solar Energy Generating Potential",
                           "max_solar_potential_county_2019" = "Max Solar Energy Generating Potential",
                           "min_solar_potential_county_2019" = "Min Solar Energy Generating Potential",
                           "mean_wind_potential_county_2019" = "Mean Wind Energy Generating Potential",
                           "max_wind_potential_county_2019" = "Max Wind Energy Generating Potential",
                           "min_wind_potential_county_2019" = "Min Wind Energy Generating Potential",
                           "mean_wind_density_potential_county_2019" = "Mean Wind Energy Density Potential",
                           "max_wind_density_potential_county_2019" = "Max Wind Energy Density Potential",
                           "min_wind_density_potential_county_2019" = "Min Wind Energy Density Potential",
                           "percentage_no_high_school_county_18_22" = "Education: No High School",
                           "percentage_high_school_county_18_22" = "Education: High School Graduates",
                           "percentage_college_county_18_22" = "Education: College Graduates",
                           "percentage_bachelor_county_18_22" = "Education: Bachelor Graduates",
                           "urban_influence_code_2013" = "Urban Influence Code",
                           "rural_urban_continuum_code_2013" = "Rural Urban Continuum Code",
                           "total_MW_2022_Q2" = "Total Energy Generation",
                           "hydro_MW_2022_Q2" = "Hydro Energy Generation",
                           "natural_gas_MW_2022_Q2" = "Natural Gas Energy Generation",
                           "coal_MW_2022_Q2" = "Coal Energy Generation",
                           "other_fossil_MW_2022_Q2" = "Other Fossil Energy Generation",
                           "solar_MW_2022_Q2" = "Solar Energy Generation",
                           "onshore_wind_MW_2022_Q2" = "Onshore Wind Energy Generation",
                           "nuclear_MW_2022_Q2" = "Nuclear Energy Generation",
                           "unemployment_rate_2022" = "Unemployment Rate 2022",
                           "unemployment_rate_2021" = "Unemployment Rate 2021",
                           "unemployment_rate_2020" = "Unemployment Rate 2020",
                           "unemployment_rate_2019" = "Unemployment Rate 2019",
                           "unemployment_rate_2018" = "Unemployment Rate 2018",
                           "all_industry_total_gdp_county_2018" = "Total GDP 2018", 
                           "all_industry_total_gdp_county_2019" = "Total GDP 2019", 
                           "all_industry_total_gdp_county_2020" = "Total GDP 2020", 
                           "all_industry_total_gdp_county_2021" = "Total GDP 2021", 
                           "all_industry_total_gdp_county_2022" = "Total GDP 2022", 
                           "government_gdp_county_2018" = "Government GDP 2018",
                           "government_gdp_county_2019" = "Government GDP 2019",
                           "government_gdp_county_2020" = "Government GDP 2020",
                           "government_gdp_county_2021" = "Government GDP 2021",
                           "government_gdp_county_2022" = "Government GDP 2022",
                           "natural_resources_mining_gdp_county_2018" = "Natural Resources Mining GDP 2018",
                           "natural_resources_mining_gdp_county_2019" = "Natural Resources Mining GDP 2019",
                           "natural_resources_mining_gdp_county_2020" = "Natural Resources Mining GDP 2020",
                           "natural_resources_mining_gdp_county_2021" = "Natural Resources Mining GDP 2021",
                           "natural_resources_mining_gdp_county_2022" = "Natural Resources Mining GDP 2022",
                           "trade_gdp_county_2018" = "Trade GDP 2018", 
                           "trade_gdp_county_2019" = "Trade GDP 2019", 
                           "trade_gdp_county_2020" = "Trade GDP 2020", 
                           "trade_gdp_county_2021" = "Trade GDP 2021", 
                           "trade_gdp_county_2022" = "Trade GDP 2022", 
                           "transportation_utilities_gdp_county_2018" = "Transportation & Utilities GDP 2018",
                           "transportation_utilities_gdp_county_2019" = "Transportation & Utilities GDP 2019",
                           "transportation_utilities_gdp_county_2020" = "Transportation & Utilities GDP 2020", 
                           "transportation_utilities_gdp_county_2021" = "Transportation & Utilities GDP 2021", 
                           "transportation_utilities_gdp_county_2022" = "Transportation & Utilities GDP 2022",
                           "manufacturing_information_gdp_county_2018" = "Manufacturing & Information GDP 2018", 
                           "manufacturing_information_gdp_county_2019" = "Manufacturing & Information GDP 2019", 
                           "manufacturing_information_gdp_county_2020" = "Manufacturing & Information GDP 2020", 
                           "manufacturing_information_gdp_county_2021" = "Manufacturing & Information GDP 2021", 
                           "manufacturing_information_gdp_county_2022" = "Manufacturing & Information GDP 2022"
  )
) +
  theme_minimal() + 
  labs(
    x = "Absolute Standardized Mean Difference",
    y = NULL
  ) +
  theme(
    legend.position = "bottom",
    legend.title = element_blank(),
    text = element_text(size = 12)
  )
ggsave("Output/love_plot_matching_investment_LASSO_all_variables.pdf", love_plot, width = 8, height = 8)

# Make a plot of the distribution of propensity scores
matched_data <- match.data(match_out)

# Create density plot
ps_plot <- ggplot(matched_data, aes(x = distance, fill = factor(ec_ind_official))) +
  geom_density(alpha = 0.5) +
  scale_fill_manual(values = c("#0072B2", "#D55E00"),
                    labels = c("Non-EC", "EC")) +
  labs(x = "Propensity Score", 
       y = "Density",
       fill = "Energy Community") +
  theme_minimal() +
  theme(legend.position = "bottom",
        text = element_text(size = 12),
        panel.grid = element_blank())
ggsave("Output/ps_density_matching_investment_LASSO_all_variables.pdf", ps_plot, width = 8, height = 5, dpi = 300)

# Calculate sample sizes
sample_table <- data.frame(
  Sample = c("Full Sample", 
             "~~~Energy Community Tracts",
             "~~~Non-Energy Community Tracts",
             "",  # Empty row for spacing
             "Matched Sample",
             "~~~Energy Community Tracts", 
             "~~~Non-Energy Community Tracts",
             "",  # Empty row for spacing
             "Dropped in Matching",
             "~~~Energy Community Tracts",
             "~~~Non-Energy Community Tracts"),
  N = c(nrow(data_census_tract),
        sum(data_census_tract$ec_ind_official == 1),
        sum(data_census_tract$ec_ind_official == 0),
        "",
        nrow(matched_data),
        sum(matched_data$ec_ind_official == 1),
        sum(matched_data$ec_ind_official == 0),
        "",
        nrow(data_census_tract) - nrow(matched_data),
        sum(data_census_tract$ec_ind_official == 1) - sum(matched_data$ec_ind_official == 1),
        sum(data_census_tract$ec_ind_official == 0) - sum(matched_data$ec_ind_official == 0))
)

# Create LaTeX table
sample_latex <- xtable(sample_table,
                      caption = "Sample Size: Propensity Score Matching",
                      label = "tab:sample_size",
                      align = c("l", "l", "r"))

# Save as .tab file
print(sample_latex,
      file = "Output/sample_size_table_investment_LASSO_all_variables.tex",
      include.rownames = FALSE,
      booktabs = TRUE,
      floating = FALSE,
      sanitize.text.function = function(x) {
        x <- gsub("~~~", "\\quad ", x, fixed = TRUE)
        return(x)
      })

matched_ids <- match.data(match_out) %>%
  pull("census_tract_id")
matched_panel <- data_census_tract %>%
  filter(census_tract_id %in% matched_ids) %>%
  select(census_tract_id)
matched_panel$matched_all_variables <- 1
data_census_tract <- left_join(data_census_tract, matched_panel, by = "census_tract_id")
data_census_tract$matched_all_variables <- ifelse(is.na(data_census_tract$matched_all_variables), 0, data_census_tract$matched_all_variables)

data_census_tract <- data_census_tract %>%
  select(census_tract_id, matched_all_variables)

write.csv(data_census_tract, "Data/constructed data/matched_panel_investment_LASSO.csv")
```

# Create matches for labor demand

```{r}
# All Variables
matching_vars <- c("area", "total_population_2020", "mean_solar_potential_county_2019", "max_solar_potential_county_2019", "min_solar_potential_county_2019", "mean_wind_potential_county_2019", "max_wind_potential_county_2019", "min_wind_potential_county_2019", "mean_wind_density_potential_county_2019", "max_wind_density_potential_county_2019", "min_wind_density_potential_county_2019", "percentage_no_high_school_county_18_22", "percentage_high_school_county_18_22", "percentage_college_county_18_22", "percentage_bachelor_county_18_22", "urban_influence_code_2013", "rural_urban_continuum_code_2013", "unemployment_rate_2018", "unemployment_rate_2019", "unemployment_rate_2020", "unemployment_rate_2021", "unemployment_rate_2022", "all_industry_total_gdp_county_2018", "all_industry_total_gdp_county_2019", "all_industry_total_gdp_county_2020", "all_industry_total_gdp_county_2021", "all_industry_total_gdp_county_2022", "government_gdp_county_2018", "government_gdp_county_2019", "government_gdp_county_2020", "government_gdp_county_2021", "government_gdp_county_2022", "natural_resources_mining_gdp_county_2018", "natural_resources_mining_gdp_county_2019", "natural_resources_mining_gdp_county_2020", "natural_resources_mining_gdp_county_2021", "natural_resources_mining_gdp_county_2022",  "trade_gdp_county_2018", "trade_gdp_county_2019", "trade_gdp_county_2020", "trade_gdp_county_2021", "trade_gdp_county_2022", "transportation_utilities_gdp_county_2018", "transportation_utilities_gdp_county_2019", "transportation_utilities_gdp_county_2020",  "transportation_utilities_gdp_county_2021", "transportation_utilities_gdp_county_2022", "manufacturing_information_gdp_county_2018", "manufacturing_information_gdp_county_2019", "manufacturing_information_gdp_county_2020", "manufacturing_information_gdp_county_2021", "manufacturing_information_gdp_county_2022", "total_MW_2022_Q2", "hydro_MW_2022_Q2", "natural_gas_MW_2022_Q2", "coal_MW_2022_Q2", "other_fossil_MW_2022_Q2", "solar_MW_2022_Q2", "onshore_wind_MW_2022_Q2", "nuclear_MW_2022_Q2")

# Step 2: Run LASSO for variable selection
# Prepare matrix of predictors
X <- data_county %>%
  select(all_of(matching_vars)) %>%
  as.matrix()

# Remove rows with any NAs
complete_rows <- complete.cases(X, data_county$ec_ind_official)
X <- X[complete_rows, ]
y <- data_county$ec_ind_official[complete_rows]

# Standardize predictors for LASSO
X_scaled <- scale(X)

# Run LASSO with cross-validation
set.seed(123)  # For reproducibility
cv_lasso <- cv.glmnet(X_scaled, y, 
                       family = "binomial",
                       alpha = 1,  # 1 = LASSO, 0 = Ridge
                       nfolds = 10)

# Plot cross-validation results
plot(cv_lasso)

# Step 3: Select variables based on LASSO
lasso_coef <- coef(cv_lasso, s = "lambda.1se")

# Extract non-zero coefficients (selected variables)
selected_vars <- rownames(lasso_coef)[which(lasso_coef != 0)]
selected_vars <- selected_vars[selected_vars != "(Intercept)"]  # Remove intercept

print(paste("LASSO selected", length(selected_vars), "variables:"))
print(selected_vars)

# Create a coefficient plot
lasso_coef_df <- as.data.frame(as.matrix(lasso_coef))
lasso_coef_df$variable <- rownames(lasso_coef_df)
names(lasso_coef_df)[1] <- "coefficient"

lasso_coef_df %>%
  mutate(variable = recode(variable,
                           "area" = "Area",
                           "total_population_2020" = "Total Population",
                           "mean_solar_potential_county_2019" = "Mean Solar Energy Generating Potential",
                           "max_solar_potential_county_2019" = "Max Solar Energy Generating Potential",
                           "min_solar_potential_county_2019" = "Min Solar Energy Generating Potential",
                           "mean_wind_potential_county_2019" = "Mean Wind Energy Generating Potential",
                           "max_wind_potential_county_2019" = "Max Wind Energy Generating Potential",
                           "min_wind_potential_county_2019" = "Min Wind Energy Generating Potential",
                           "mean_wind_density_potential_county_2019" = "Mean Wind Energy Density Potential",
                           "max_wind_density_potential_county_2019" = "Max Wind Energy Density Potential",
                           "min_wind_density_potential_county_2019" = "Min Wind Energy Density Potential",
                           "percentage_no_high_school_county_18_22" = "Education: No High School",
                           "percentage_high_school_county_18_22" = "Education: High School Graduates",
                           "percentage_college_county_18_22" = "Education: College Graduates",
                           "percentage_bachelor_county_18_22" = "Education: Bachelor Graduates",
                           "urban_influence_code_2013" = "Urban Influence Code",
                           "rural_urban_continuum_code_2013" = "Rural Urban Continuum Code",
                           "total_MW_2022_Q2" = "Total Energy Generation",
                           "hydro_MW_2022_Q2" = "Hydro Energy Generation",
                           "natural_gas_MW_2022_Q2" = "Natural Gas Energy Generation",
                           "coal_MW_2022_Q2" = "Coal Energy Generation",
                           "other_fossil_MW_2022_Q2" = "Other Fossil Energy Generation",
                           "solar_MW_2022_Q2" = "Solar Energy Generation",
                           "onshore_wind_MW_2022_Q2" = "Onshore Wind Energy Generation",
                           "nuclear_MW_2022_Q2" = "Nuclear Energy Generation",
                           "unemployment_rate_2022" = "Unemployment Rate 2022",
                           "unemployment_rate_2021" = "Unemployment Rate 2021",
                           "unemployment_rate_2020" = "Unemployment Rate 2020",
                           "unemployment_rate_2019" = "Unemployment Rate 2019",
                           "unemployment_rate_2018" = "Unemployment Rate 2018",
                           "all_industry_total_gdp_county_2018" = "Total GDP 2018", 
                           "all_industry_total_gdp_county_2019" = "Total GDP 2019", 
                           "all_industry_total_gdp_county_2020" = "Total GDP 2020", 
                           "all_industry_total_gdp_county_2021" = "Total GDP 2021", 
                           "all_industry_total_gdp_county_2022" = "Total GDP 2022", 
                           "government_gdp_county_2018" = "Government GDP 2018",
                           "government_gdp_county_2019" = "Government GDP 2019",
                           "government_gdp_county_2020" = "Government GDP 2020",
                           "government_gdp_county_2021" = "Government GDP 2021",
                           "government_gdp_county_2022" = "Government GDP 2022",
                           "natural_resources_mining_gdp_county_2018" = "Natural Resources Mining GDP 2018",
                           "natural_resources_mining_gdp_county_2019" = "Natural Resources Mining GDP 2019",
                           "natural_resources_mining_gdp_county_2020" = "Natural Resources Mining GDP 2020",
                           "natural_resources_mining_gdp_county_2021" = "Natural Resources Mining GDP 2021",
                           "natural_resources_mining_gdp_county_2022" = "Natural Resources Mining GDP 2022",
                           "trade_gdp_county_2018" = "Trade GDP 2018", 
                           "trade_gdp_county_2019" = "Trade GDP 2019", 
                           "trade_gdp_county_2020" = "Trade GDP 2020", 
                           "trade_gdp_county_2021" = "Trade GDP 2021", 
                           "trade_gdp_county_2022" = "Trade GDP 2022", 
                           "transportation_utilities_gdp_county_2018" = "Transportation & Utilities GDP 2018",
                           "transportation_utilities_gdp_county_2019" = "Transportation & Utilities GDP 2019",
                           "transportation_utilities_gdp_county_2020" = "Transportation & Utilities GDP 2020", 
                           "transportation_utilities_gdp_county_2021" = "Transportation & Utilities GDP 2021", 
                           "transportation_utilities_gdp_county_2022" = "Transportation & Utilities GDP 2022",
                           "manufacturing_information_gdp_county_2018" = "Manufacturing & Information GDP 2018", 
                           "manufacturing_information_gdp_county_2019" = "Manufacturing & Information GDP 2019", 
                           "manufacturing_information_gdp_county_2020" = "Manufacturing & Information GDP 2020", 
                           "manufacturing_information_gdp_county_2021" = "Manufacturing & Information GDP 2021", 
                           "manufacturing_information_gdp_county_2022" = "Manufacturing & Information GDP 2022")) %>%
  filter(variable != "(Intercept)" & coefficient != 0) %>%
  ggplot(aes(x = reorder(variable, abs(coefficient)), y = coefficient)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  coord_flip() +
  labs(x = "Variable", y = "LASSO Coefficient") +
  theme_minimal()
ggsave("Output/lasso_coefficients_labor_demand_all_variables.png", width = 8, height = 6)

# Step 4: Alternative - show coefficients across lambda values
lasso_full <- glmnet(X_scaled, y, family = "binomial", alpha = 1)
plot(lasso_full, xvar = "lambda", label = TRUE)

# Step 5: Run matching with LASSO-selected variables
# Create formula with selected variables
match_formula <- as.formula(paste("ec_ind_official ~", 
                                  paste(selected_vars, collapse = " + ")))

# Perform matching
match_out <- matchit(
  match_formula,
  data = data_county[complete_rows, ],  # Use same subset as LASSO
  method = "nearest",
  distance = "logit",
  replace = FALSE,
  caliper = 0.1,
  ratio = 1
)

love_plot <- love.plot(
  match_out,
  thresholds = c(m = 0.1),
  abs = TRUE,
  colors = c("red", "blue"),
  shapes = c(19, 17),
  title = NULL,
  # Provide a named vector of old names -> new labels
  var.names = c(
                           "area" = "Area",
                           "total_population_2020" = "Total Population",
                           "mean_solar_potential_county_2019" = "Mean Solar Energy Generating Potential",
                           "max_solar_potential_county_2019" = "Max Solar Energy Generating Potential",
                           "min_solar_potential_county_2019" = "Min Solar Energy Generating Potential",
                           "mean_wind_potential_county_2019" = "Mean Wind Energy Generating Potential",
                           "max_wind_potential_county_2019" = "Max Wind Energy Generating Potential",
                           "min_wind_potential_county_2019" = "Min Wind Energy Generating Potential",
                           "mean_wind_density_potential_county_2019" = "Mean Wind Energy Density Potential",
                           "max_wind_density_potential_county_2019" = "Max Wind Energy Density Potential",
                           "min_wind_density_potential_county_2019" = "Min Wind Energy Density Potential",
                           "percentage_no_high_school_county_18_22" = "Education: No High School",
                           "percentage_high_school_county_18_22" = "Education: High School Graduates",
                           "percentage_college_county_18_22" = "Education: College Graduates",
                           "percentage_bachelor_county_18_22" = "Education: Bachelor Graduates",
                           "urban_influence_code_2013" = "Urban Influence Code",
                           "rural_urban_continuum_code_2013" = "Rural Urban Continuum Code",
                           "total_MW_2022_Q2" = "Total Energy Generation",
                           "hydro_MW_2022_Q2" = "Hydro Energy Generation",
                           "natural_gas_MW_2022_Q2" = "Natural Gas Energy Generation",
                           "coal_MW_2022_Q2" = "Coal Energy Generation",
                           "other_fossil_MW_2022_Q2" = "Other Fossil Energy Generation",
                           "solar_MW_2022_Q2" = "Solar Energy Generation",
                           "onshore_wind_MW_2022_Q2" = "Onshore Wind Energy Generation",
                           "nuclear_MW_2022_Q2" = "Nuclear Energy Generation",
                           "unemployment_rate_2022" = "Unemployment Rate 2022",
                           "unemployment_rate_2021" = "Unemployment Rate 2021",
                           "unemployment_rate_2020" = "Unemployment Rate 2020",
                           "unemployment_rate_2019" = "Unemployment Rate 2019",
                           "unemployment_rate_2018" = "Unemployment Rate 2018",
                           "all_industry_total_gdp_county_2018" = "Total GDP 2018", 
                           "all_industry_total_gdp_county_2019" = "Total GDP 2019", 
                           "all_industry_total_gdp_county_2020" = "Total GDP 2020", 
                           "all_industry_total_gdp_county_2021" = "Total GDP 2021", 
                           "all_industry_total_gdp_county_2022" = "Total GDP 2022", 
                           "government_gdp_county_2018" = "Government GDP 2018",
                           "government_gdp_county_2019" = "Government GDP 2019",
                           "government_gdp_county_2020" = "Government GDP 2020",
                           "government_gdp_county_2021" = "Government GDP 2021",
                           "government_gdp_county_2022" = "Government GDP 2022",
                           "natural_resources_mining_gdp_county_2018" = "Natural Resources Mining GDP 2018",
                           "natural_resources_mining_gdp_county_2019" = "Natural Resources Mining GDP 2019",
                           "natural_resources_mining_gdp_county_2020" = "Natural Resources Mining GDP 2020",
                           "natural_resources_mining_gdp_county_2021" = "Natural Resources Mining GDP 2021",
                           "natural_resources_mining_gdp_county_2022" = "Natural Resources Mining GDP 2022",
                           "trade_gdp_county_2018" = "Trade GDP 2018", 
                           "trade_gdp_county_2019" = "Trade GDP 2019", 
                           "trade_gdp_county_2020" = "Trade GDP 2020", 
                           "trade_gdp_county_2021" = "Trade GDP 2021", 
                           "trade_gdp_county_2022" = "Trade GDP 2022", 
                           "transportation_utilities_gdp_county_2018" = "Transportation & Utilities GDP 2018",
                           "transportation_utilities_gdp_county_2019" = "Transportation & Utilities GDP 2019",
                           "transportation_utilities_gdp_county_2020" = "Transportation & Utilities GDP 2020", 
                           "transportation_utilities_gdp_county_2021" = "Transportation & Utilities GDP 2021", 
                           "transportation_utilities_gdp_county_2022" = "Transportation & Utilities GDP 2022",
                           "manufacturing_information_gdp_county_2018" = "Manufacturing & Information GDP 2018", 
                           "manufacturing_information_gdp_county_2019" = "Manufacturing & Information GDP 2019", 
                           "manufacturing_information_gdp_county_2020" = "Manufacturing & Information GDP 2020", 
                           "manufacturing_information_gdp_county_2021" = "Manufacturing & Information GDP 2021", 
                           "manufacturing_information_gdp_county_2022" = "Manufacturing & Information GDP 2022"
  )
) +
  theme_minimal() + 
  labs(
    x = "Absolute Standardized Mean Difference",
    y = NULL
  ) +
  theme(
    legend.position = "bottom",
    legend.title = element_blank(),
    text = element_text(size = 12)
  )
ggsave("Output/love_plot_matching_labor_demand_LASSO_all_variables.pdf", love_plot, width = 8, height = 8)

# Make a plot of the distribution of propensity scores
matched_data <- match.data(match_out)

# Create density plot
ps_plot <- ggplot(matched_data, aes(x = distance, fill = factor(ec_ind_official))) +
  geom_density(alpha = 0.5) +
  scale_fill_manual(values = c("#0072B2", "#D55E00"),
                    labels = c("Non-EC", "EC")) +
  labs(x = "Propensity Score", 
       y = "Density",
       fill = "Energy Community") +
  theme_minimal() +
  theme(legend.position = "bottom",
        text = element_text(size = 12),
        panel.grid = element_blank())
ggsave("Output/ps_density_matching_labor_demand_LASSO_all_variables.pdf", ps_plot, width = 8, height = 5, dpi = 300)

# Calculate sample sizes
sample_table <- data.frame(
  Sample = c("Full Sample", 
             "~~~Energy Community Counties",
             "~~~Non-Energy Community Counties",
             "",  # Empty row for spacing
             "Matched Sample",
             "~~~Energy Community Counties", 
             "~~~Non-Energy Community Counties",
             "",  # Empty row for spacing
             "Dropped in Matching",
             "~~~Energy Community Counties",
             "~~~Non-Energy Community Counties"),
  N = c(nrow(data_county),
        sum(data_county$ec_ind_official == 1),
        sum(data_county$ec_ind_official == 0),
        "",
        nrow(matched_data),
        sum(matched_data$ec_ind_official == 1),
        sum(matched_data$ec_ind_official == 0),
        "",
        nrow(data_county) - nrow(matched_data),
        sum(data_county$ec_ind_official == 1) - sum(matched_data$ec_ind_official == 1),
        sum(data_county$ec_ind_official == 0) - sum(matched_data$ec_ind_official == 0))
)

# Create LaTeX table
sample_latex <- xtable(sample_table,
                      caption = "Sample Size: Propensity Score Matching",
                      label = "tab:sample_size",
                      align = c("l", "l", "r"))

# Save as .tab file
print(sample_latex,
      file = "Output/sample_size_table_labor_demand_LASSO_all_variables.tex",
      include.rownames = FALSE,
      booktabs = TRUE,
      floating = FALSE,
      sanitize.text.function = function(x) {
        x <- gsub("~~~", "\\quad ", x, fixed = TRUE)
        return(x)
      })

matched_ids <- match.data(match_out) %>%
  pull("county_id")
matched_panel <- data_county %>%
  filter(county_id %in% matched_ids) %>%
  select(county_id)
matched_panel$matched_all_variables <- 1
data_county <- left_join(data_county, matched_panel, by = "county_id")
data_county$matched_all_variables <- ifelse(is.na(data_county$matched_all_variables), 0, data_county$matched_all_variables)

data_county <- data_county %>%
  select(county_id, matched_all_variables)

write.csv(data_county, "Data/constructed data/matched_panel_labor_demand_LASSO.csv")
```
