---
title: "04_build_labordemand_data"
output: html_document
date: "2025-07-16"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Geographic regions

Here, we lay the groundwork by providing all the geographic regions in the dataset.

```{r}
# Add the census tracts
census_tracts <- sf::st_read("Data/raw data/tlgdb_2020_a_us_substategeo.gdb", layer = "Census_Tract")
census_tracts <- census_tracts %>%
  select("GEOID", "NAMELSAD", "SHAPE") %>%
  rename("census_tract_id" = "GEOID",
         "census_tract_name" = "NAMELSAD")
census_tracts$county_id <- str_sub(census_tracts$census_tract_id, 1, 5)
census_tracts$state_id <- str_sub(census_tracts$census_tract_id, 1, 2)
counties <- sf::st_read("Data/raw data/tlgdb_2020_a_us_substategeo.gdb", layer = "County")
counties <- counties %>%
  select("GEOID", "NAMELSAD") %>%
  rename("county_id" = "GEOID",
         "county_name" = "NAMELSAD") %>%
  st_drop_geometry()
census_tracts <- left_join(census_tracts, counties, by = "county_id")

rm(counties)
```

## Add the 2023 (cohort 1) energy communities: IRS notice 2023-29

```{r}
coal_closure <- read.csv("Data/raw data/IRA_Coal_Closure_Energy_Comm_2023v2/Coal_Closure_Energy_Communities_2023v2.csv")
coal_closure$geoid_tract_2020 <- str_pad(coal_closure$geoid_tract_2020, 11, pad = "0")
EC_employ <- read.csv("Data/raw data/MSA_NMSA_FEE_EC_Status_2023v2/MSA_NMSA_FFE_EC_2023v2.csv")
EC_employ$geoid_cty_2020 <- str_pad(EC_employ$geoid_cty_2020, 5, pad = "0")
coal_closure_mine <- coal_closure %>%
  filter(Tract_Status %in% c("is an energy community due to a coal mine closure"))
coal_closure_mine <- unique(coal_closure_mine$geoid_tract_2020)
coal_closure_generator <- coal_closure %>%
  filter(Generator_Closure == "Yes")
coal_closure_generator <- unique(coal_closure_generator$geoid_tract_2020)
coal_closure_adjacent <- coal_closure %>%
  filter(Adjacent_to_Closure == "Yes")
coal_closure_adjacent <- unique(coal_closure_adjacent$geoid_tract_2020)
EC_employ <- unique(EC_employ[EC_employ$EC_qual_status == "Yes", ]$geoid_cty_2020)

data <- census_tracts

data$coal_mine_closure_official_cohort_1 <- ifelse(data$census_tract_id %in% coal_closure_mine, 1, 0)
data$generator_closure_official_cohort_1 <- ifelse(data$census_tract_id %in% coal_closure_generator, 1, 0)
data$adjacent_closure_official_cohort_1 <- ifelse(data$census_tract_id %in% coal_closure_adjacent, 1, 0)
data$unemployment_official_msa_cohort_1 <- ifelse(data$county_id %in% EC_employ, 1, 0)

rm(coal_closure, EC_employ, coal_closure_adjacent, coal_closure_generator, coal_closure_mine)
```

## Add the 2023 (cohort 2) energy communities: IRS notice 2024-30

```{r}
coal_closure <- read.csv("Data/raw data/IRA_Coal_Closure_Energy_Comm_2023v2/Coal_Closure_Energy_Communities_2023v2.csv")
coal_closure$geoid_tract_2020 <- str_pad(coal_closure$geoid_tract_2020, 11, pad = "0")
EC_employ <- read.csv("Data/raw data/MSA_NMSA_EC_FFE_Status_v2023_3/MSA_NonMSA_EnergyCommunities_FossilFuelEmp_2023v3.csv")
EC_employ$geoid_county_2020 <- str_pad(EC_employ$geoid_county_2020, 5, pad = "0")
coal_closure_mine <- coal_closure %>%
  filter(Tract_Status %in% c("is an energy community due to a coal mine closure"))
coal_closure_mine <- unique(coal_closure_mine$geoid_tract_2020)
coal_closure_generator <- coal_closure %>%
  filter(Generator_Closure == "Yes")
coal_closure_generator <- unique(coal_closure_generator$geoid_tract_2020)
coal_closure_adjacent <- coal_closure %>%
  filter(Adjacent_to_Closure == "Yes")
coal_closure_adjacent <- unique(coal_closure_adjacent$geoid_tract_2020)
EC_employ <- unique(EC_employ[EC_employ$ec_qual_status == "Yes", ]$geoid_county_2020)

data$coal_mine_closure_official_cohort_2 <- ifelse(data$census_tract_id %in% coal_closure_mine, 1, 0)
data$generator_closure_official_cohort_2 <- ifelse(data$census_tract_id %in% coal_closure_generator, 1, 0)
data$adjacent_closure_official_cohort_2 <- ifelse(data$census_tract_id %in% coal_closure_adjacent, 1, 0)
data$unemployment_official_msa_cohort_2 <- ifelse(data$county_id %in% EC_employ, 1, 0)

rm(coal_closure, EC_employ, coal_closure_adjacent, coal_closure_generator, coal_closure_mine)
```

## Add the 2024 (cohort 3) energy communities: IRS notice 2024-48

```{r}
coal_closure <- read.csv("Data/raw data/Coal_Closures_EnergyComm_v2024_1/IRA_EnergyComm_CTracts_CoalClosures_v2024_1.csv")
coal_closure$geoid_tract_2020 <- str_pad(coal_closure$geoid_tract_2020, 11, pad = "0")
EC_employ <- read.csv("Data/raw data/MSA_NMSA_EC_FFE_v2024_1/MSA_NonMSA_EnergyCommunities_FossilFuelEmp_v2024_1.csv")
EC_employ$geoid_county_2020 <- str_pad(EC_employ$geoid_county_2020, 5, pad = "0")
coal_closure_mine <- coal_closure %>%
  filter(Mine_Closure == "Yes")
coal_closure_mine <- unique(coal_closure_mine$geoid_tract_2020)
coal_closure_generator <- coal_closure %>%
  filter(Generator_Closure == "Yes")
coal_closure_generator <- unique(coal_closure_generator$geoid_tract_2020)
coal_closure_adjacent <- coal_closure %>%
  filter(Adjacent_to_Closure == "Yes")
coal_closure_adjacent <- unique(coal_closure_adjacent$geoid_tract_2020)
EC_employ <- unique(EC_employ[EC_employ$ec_qual_status == "Yes", ]$geoid_county_2020)

data$coal_mine_closure_official_cohort_3 <- ifelse(data$census_tract_id %in% coal_closure_mine, 1, 0)
data$generator_closure_official_cohort_3 <- ifelse(data$census_tract_id %in% coal_closure_generator, 1, 0)
data$adjacent_closure_official_cohort_3 <- ifelse(data$census_tract_id %in% coal_closure_adjacent, 1, 0)
data$unemployment_official_msa_cohort_3 <- ifelse(data$county_id %in% EC_employ, 1, 0)

rm(coal_closure, EC_employ, coal_closure_adjacent, coal_closure_generator, coal_closure_mine)
```

## Add binary indicator for energy communities

```{r}
data <- data %>%
  mutate(ec_ind_official_cohort_1 = ifelse((coal_mine_closure_official_cohort_1 == 1 | 
                                   generator_closure_official_cohort_1 == 1 | 
                                   adjacent_closure_official_cohort_1 == 1) |
                                   unemployment_official_msa_cohort_1 == 1, 
                                   1, 0))

data <- data %>%
  mutate(ec_ind_official_cohort_2 = ifelse((coal_mine_closure_official_cohort_2 == 1 | 
                                   generator_closure_official_cohort_2 == 1 | 
                                   adjacent_closure_official_cohort_2 == 1) |
                                   unemployment_official_msa_cohort_2 == 1, 
                                   1, 0))

data <- data %>%
  mutate(ec_ind_official_cohort_3 = ifelse((coal_mine_closure_official_cohort_3 == 1 | 
                                   generator_closure_official_cohort_3 == 1 | 
                                   adjacent_closure_official_cohort_3 == 1) |
                                   unemployment_official_msa_cohort_3 == 1, 
                                   1, 0))
```

## Create a time-series aspect

```{r}
## Land Surface Area
data <- st_as_sf(data)
data$area <- st_area(data)/1000

# We should have a row for each quarter-census tract combination
quarters <- seq.Date(from = as.Date("2015-01-01"), to = as.Date("2024-12-31"), by = "quarter")
census_tracts <- unique(data$census_tract_id)
all_combinations <- expand.grid(census_tract_id = census_tracts, quarter_date = quarters)
data <- merge(all_combinations, data, by = "census_tract_id", all.x = TRUE)
data$year <- substr(data$quarter, 1, 4)
data <- data %>%
  mutate(quarter = quarters(quarter_date))

rm(census_tracts, all_combinations, quarters)
```

## Add the Population by census tract

```{r}
population <- read.csv("Data/raw data/DECENNIALDP2020.DP1_2024-04-08T040530/DECENNIALDP2020.DP1-Data.csv")
population <- population[-1, ]
population <- subset(population, select = c("GEO_ID", "NAME", "DP1_0001C", "DP1_0006C", "DP1_0007C", "DP1_0008C", "DP1_0009C", "DP1_0010C", "DP1_0011C", "DP1_0012C", "DP1_0013C", "DP1_0014C"))
population <- population %>%
  rename("total_population_2020" = "DP1_0001C")
population$working_age_population_2020 <- as.numeric(population$DP1_0006C) + as.numeric(population$DP1_0007C) + as.numeric(population$DP1_0008C) + as.numeric(population$DP1_0009C) + as.numeric(population$DP1_0010C) + as.numeric(population$DP1_0011C) + as.numeric(population$DP1_0012C) + as.numeric(population$DP1_0013C) + as.numeric(population$DP1_0014C)
population$census_tract_id <- sub(".*US", "", population$GEO_ID)
population <- population %>%
  select(census_tract_id, total_population_2020, working_age_population_2020)

# Merge the demographics with the complete dataset
data <- left_join(data, population, by = "census_tract_id")

rm(population)
```

## Transform the dataframe so that we have counties as the basis

```{r}
data <- data %>%
  st_drop_geometry() %>%
  select(census_tract_id, county_id, county_name, state_id, coal_mine_closure_official_cohort_1, generator_closure_official_cohort_1, adjacent_closure_official_cohort_1, unemployment_official_msa_cohort_1, coal_mine_closure_official_cohort_2, generator_closure_official_cohort_2, adjacent_closure_official_cohort_2, unemployment_official_msa_cohort_2, coal_mine_closure_official_cohort_3, generator_closure_official_cohort_3, adjacent_closure_official_cohort_3, unemployment_official_msa_cohort_3, ec_ind_official_cohort_1, ec_ind_official_cohort_2, ec_ind_official_cohort_3, area, year, quarter, total_population_2020, working_age_population_2020) %>% unique()
data$area <- as.numeric(data$area)
data$total_population_2020 <- as.numeric(data$total_population_2020)

data <- data %>%
  group_by(county_id, year, quarter) %>%
  summarise(county_name = first(county_name),
            state_id = first(state_id),
            ec_ind_official_cohort_1_percentage = mean(ec_ind_official_cohort_1, na.rm = TRUE),
            ec_ind_official_cohort_2_percentage = mean(ec_ind_official_cohort_2, na.rm = TRUE),
            ec_ind_official_cohort_3_percentage = mean(ec_ind_official_cohort_3, na.rm = TRUE),
            ec_ind_official_cohort_1_area_weighted = weighted.mean(ec_ind_official_cohort_1, area, na.rm = TRUE),
            ec_ind_official_cohort_2_area_weighted = weighted.mean(ec_ind_official_cohort_2, area, na.rm = TRUE),
            ec_ind_official_cohort_3_area_weighted = weighted.mean(ec_ind_official_cohort_3, area, na.rm = TRUE),
            ec_ind_official_cohort_1_population_weighted = weighted.mean(ec_ind_official_cohort_1, total_population_2020, na.rm = TRUE),
            ec_ind_official_cohort_2_population_weighted = weighted.mean(ec_ind_official_cohort_2, total_population_2020, na.rm = TRUE),
            ec_ind_official_cohort_3_population_weighted = weighted.mean(ec_ind_official_cohort_3, total_population_2020, na.rm = TRUE),
            ec_ind_official_cohort_1_working_population_weighted = weighted.mean(ec_ind_official_cohort_1, working_age_population_2020, na.rm = TRUE),
            ec_ind_official_cohort_2_working_population_weighted = weighted.mean(ec_ind_official_cohort_2, working_age_population_2020, na.rm = TRUE),
            ec_ind_official_cohort_3_working_population_weighted = weighted.mean(ec_ind_official_cohort_3, working_age_population_2020, na.rm = TRUE),
            area = sum(area, na.rm = TRUE),
            total_population_2020 = sum(total_population_2020, na.rm = TRUE),
            working_age_population_2020 = sum(working_age_population_2020, na.rm = TRUE))
```

## Add the number of employed and labor force

```{r}
# Add the number of employed and labor force
unemployment <- read.csv("Data/raw data/Unemployment2023.csv")
civilian_labor_force <- unemployment %>%
  filter(Attribute %in% c("Civilian_labor_force_2010", "Civilian_labor_force_2011", "Civilian_labor_force_2012", "Civilian_labor_force_2013", "Civilian_labor_force_2014", "Civilian_labor_force_2015", "Civilian_labor_force_2016", "Civilian_labor_force_2017", "Civilian_labor_force_2018", "Civilian_labor_force_2019", "Civilian_labor_force_2020", "Civilian_labor_force_2021", "Civilian_labor_force_2022", "Civilian_labor_force_2023"))
civilian_labor_force$year <- sub(".*_(\\d{4})$", "\\1", civilian_labor_force$Attribute)
civilian_labor_force <- civilian_labor_force %>%
  select(FIPS_Code, year, Value) %>%
  rename("county_id" = "FIPS_Code",
         "civilian_labor_force" = "Value")
employed <- unemployment %>%
  filter(Attribute %in% c("Employed_2010", "Employed_2011", "Employed_2012", "Employed_2013", "Employed_2014", "Employed_2015", "Employed_2016", "Employed_2017", "Employed_2018", "Employed_2019", "Employed_2020", "Employed_2021", "Employed_2022", "Employed_2023"))
employed$year <- sub(".*_(\\d{4})$", "\\1", employed$Attribute)
employed <- employed %>%
  select(FIPS_Code, year, Value) %>%
  rename("county_id" = "FIPS_Code",
         "employed" = "Value")
  
employed <- left_join(employed, civilian_labor_force, by = c("county_id", "year"))
employed$county_id <- str_pad(employed$county_id, 5, pad = "0")
employed$year <- as.numeric(employed$year)

data$year <- as.numeric(data$year)
data$county_id <- str_pad(data$county_id, 5, pad = "0")

data <- left_join(data, employed, by = c("county_id", "year"))

rm(employed)
```

## Add the solar labor demand

```{r}
solar_employment_2015_16 <- read.csv("Data/lightcast data/Create_Solar_Dataset_2015_16.csv")
colnames(solar_employment_2015_16) <- solar_employment_2015_16[1, ]
solar_employment_2015_16 <- solar_employment_2015_16[-1, ]
solar_employment_2017_18 <- read.csv("Data/lightcast data/Create_Solar_Dataset_2017_18.csv")
colnames(solar_employment_2017_18) <- solar_employment_2017_18[1, ]
solar_employment_2017_18 <- solar_employment_2017_18[-1, ]
solar_employment_2019_20 <- read.csv("Data/lightcast data/Create_Solar_Dataset_2019_20.csv")
colnames(solar_employment_2019_20) <- solar_employment_2019_20[1, ]
solar_employment_2019_20 <- solar_employment_2019_20[-1, ]
solar_employment_2021_22 <- read.csv("Data/lightcast data/Create_Solar_Dataset_2021_22.csv")
colnames(solar_employment_2021_22) <- solar_employment_2021_22[1, ]
solar_employment_2021_22 <- solar_employment_2021_22[-1, ]
solar_employment_2023_24 <- read.csv("Data/lightcast data/Create_Solar_Dataset_2023_24.csv")
colnames(solar_employment_2023_24) <- solar_employment_2023_24[1, ]
solar_employment_2023_24 <- solar_employment_2023_24[-1, ]

solar_employment <- rbind(solar_employment_2015_16, solar_employment_2017_18)
solar_employment <- rbind(solar_employment, solar_employment_2019_20)
solar_employment <- rbind(solar_employment, solar_employment_2021_22)
solar_employment <- rbind(solar_employment, solar_employment_2023_24)

# How many solar job vacancies each year
solar_employment_annual <- solar_employment %>% 
  select(year, total_count) %>%
  group_by(year) %>%
  summarise(total_count_solar = sum(as.numeric(total_count), na.rm = TRUE))

solar_employment_skill_type <- solar_employment %>%
  filter(!is.na(career_type)) %>%
  group_by(county_id, year, month, career_type) %>%
  summarise(total_count = sum(as.numeric(total_count)), .groups = 'drop') %>%
  pivot_wider(names_from = career_type, values_from = total_count, values_fill = 0) %>%
  rename_with(~ str_replace_all(., " ", "_"), everything()) %>%
  mutate(
    county_id = str_pad(as.numeric(sub("^US", "", county_id)), 5, pad = "0"),
    low_skilled_solar_technologies = `9`, 
    mid_skilled_solar_technologies = rowSums(select(., `5`, `null`, `6`, `4`), na.rm = TRUE),
    high_skilled_solar_technologies = rowSums(select(., `1`, `3`, `2`), na.rm = TRUE),
    solar_technologies_job_vacancies = rowSums(select(., `null`, `1`, `2`, `3`, `4`, `5`, `6`, `7`, `8`, `9`), na.rm = TRUE)
  )

solar_employment_skill_type$year <- as.numeric(solar_employment_skill_type$year)
solar_employment_skill_type$month <- as.numeric(solar_employment_skill_type$month)

solar_employment_skill_type_quarterly <- solar_employment_skill_type %>%
  select(county_id, year, month, solar_technologies_job_vacancies, low_skilled_solar_technologies, mid_skilled_solar_technologies, high_skilled_solar_technologies) %>%
  mutate(quarter = quarter(month)) %>%  # Convert month to quarter
  select(-month) %>%  # Remove the month column
  group_by(county_id, year, quarter) %>%  # Group by county_id, year, and quarter
  summarise(across(everything(), \(x) sum(x, na.rm = TRUE)), .groups = "drop")

solar_employment_skill_type_quarterly$quarter <- str_pad(solar_employment_skill_type_quarterly$quarter, 2, pad = "Q")

data <- left_join(data, solar_employment_skill_type_quarterly, by = c("county_id", "year", "quarter"))

rm(solar_employment_2017_18, solar_employment_2019_20, solar_employment_2021_22, solar_employment_2023_24, solar_employment_skill_type, solar_employment_skill_type_quarterly, solar_employment_2015_16, solar_employment)
```

## Add wind labor demand

```{r}
wind_employment_2015_16 <- read.csv("Data/lightcast data/Create_Wind_Dataset_2015_16.csv")
colnames(wind_employment_2015_16) <- wind_employment_2015_16[1, ]
wind_employment_2015_16 <- wind_employment_2015_16[-1, ]
wind_employment_2017_18 <- read.csv("Data/lightcast data/Create_Wind_Dataset_2017_18.csv")
colnames(wind_employment_2017_18) <- wind_employment_2017_18[1, ]
wind_employment_2017_18 <- wind_employment_2017_18[-1, ]
wind_employment_2019_20 <- read.csv("Data/lightcast data/Create_Wind_Dataset_2019_20.csv")
colnames(wind_employment_2019_20) <- wind_employment_2019_20[1, ]
wind_employment_2019_20 <- wind_employment_2019_20[-1, ]
wind_employment_2021_22 <- read.csv("Data/lightcast data/Create_Wind_Dataset_2021_22.csv")
colnames(wind_employment_2021_22) <- wind_employment_2021_22[1, ]
wind_employment_2021_22 <- wind_employment_2021_22[-1, ]
wind_employment_2023_24 <- read.csv("Data/lightcast data/Create_Wind_Dataset_2023_24.csv")
colnames(wind_employment_2023_24) <- wind_employment_2023_24[1, ]
wind_employment_2023_24 <- wind_employment_2023_24[-1, ]

wind_employment <- rbind(wind_employment_2015_16, wind_employment_2017_18)
wind_employment <- rbind(wind_employment, wind_employment_2019_20)
wind_employment <- rbind(wind_employment, wind_employment_2021_22)
wind_employment <- rbind(wind_employment, wind_employment_2023_24)

wind_employment_skill_type <- wind_employment %>%
  filter(!is.na(career_type)) %>%
  group_by(county_id, year, month, career_type) %>%
  summarise(total_count = sum(as.numeric(total_count)), .groups = 'drop') %>%
  pivot_wider(names_from = career_type, values_from = total_count, values_fill = 0) %>%
  rename_with(~ str_replace_all(., " ", "_"), everything()) %>%
  mutate(
    county_id = str_pad(as.numeric(sub("^US", "", county_id)), 5, pad = "0"),
    low_skilled_wind_technologies = `9`, 
    mid_skilled_wind_technologies = rowSums(select(., `4`, `5`, `6`, `7`, `8`), na.rm = TRUE),
    high_skilled_wind_technologies = rowSums(select(., `1`, `2`, `3`), na.rm = TRUE),
    wind_technologies_job_vacancies = rowSums(select(., `null`, `1`, `2`, `3`, `4`, `5`, `6`, `7`, `8`, `9`), na.rm = TRUE)
  )

wind_employment_skill_type$year <- as.numeric(wind_employment_skill_type$year)
wind_employment_skill_type$month <- as.numeric(wind_employment_skill_type$month)

wind_employment_skill_type_quarterly <- wind_employment_skill_type %>%
  select(county_id, year, month, wind_technologies_job_vacancies, low_skilled_wind_technologies, mid_skilled_wind_technologies, high_skilled_wind_technologies) %>%
  mutate(quarter = quarter(month)) %>%  # Convert month to quarter
  select(-month) %>%  # Remove the month column
  group_by(county_id, year, quarter) %>%  # Group by county_id, year, and quarter
  summarise(across(everything(), \(x) sum(x, na.rm = TRUE)), .groups = "drop")

wind_employment_skill_type_quarterly$quarter <- str_pad(wind_employment_skill_type_quarterly$quarter, 2, pad = "Q")

data <- left_join(data, wind_employment_skill_type_quarterly, by = c("county_id", "year", "quarter"))
rm(wind_employment_2017_18, wind_employment_2019_20, wind_employment_2021_22, wind_employment_2023_24, wind_employment_skill_type, wind_employment_skill_type_quarterly, wind_employment_2015_16, wind_employment)
```

## Add Y02E10 labor demand

```{r}
Y02E10_employment_2015_16 <- read.csv("Data/lightcast data/Create_Y02E10_Dataset_2015_16.csv")
colnames(Y02E10_employment_2015_16) <- Y02E10_employment_2015_16[1, ]
Y02E10_employment_2015_16 <- Y02E10_employment_2015_16[-1, ]
Y02E10_employment_2017_18 <- read.csv("Data/lightcast data/Create_Y02E10_Dataset_2017_18.csv")
colnames(Y02E10_employment_2017_18) <- Y02E10_employment_2017_18[1, ]
Y02E10_employment_2017_18 <- Y02E10_employment_2017_18[-1, ]
Y02E10_employment_2019_20 <- read.csv("Data/lightcast data/Create_Y02E10_Dataset_2019_20.csv")
colnames(Y02E10_employment_2019_20) <- Y02E10_employment_2019_20[1, ]
Y02E10_employment_2019_20 <- Y02E10_employment_2019_20[-1, ]
Y02E10_employment_2021_22 <- read.csv("Data/lightcast data/Create_Y02E10_Dataset_2021_22.csv")
colnames(Y02E10_employment_2021_22) <- Y02E10_employment_2021_22[1, ]
Y02E10_employment_2021_22 <- Y02E10_employment_2021_22[-1, ]
Y02E10_employment_2023_24 <- read.csv("Data/lightcast data/Create_Y02E10_Dataset_2023_24.csv")
colnames(Y02E10_employment_2023_24) <- Y02E10_employment_2023_24[1, ]
Y02E10_employment_2023_24 <- Y02E10_employment_2023_24[-1, ]

Y02E10_employment <- rbind(Y02E10_employment_2015_16, Y02E10_employment_2017_18)
Y02E10_employment <- rbind(Y02E10_employment, Y02E10_employment_2019_20)
Y02E10_employment <- rbind(Y02E10_employment, Y02E10_employment_2021_22)
Y02E10_employment <- rbind(Y02E10_employment, Y02E10_employment_2023_24)

Y02E10_employment_skill_type <- Y02E10_employment %>%
  filter(!is.na(career_type)) %>%
  group_by(county_id, year, month, career_type) %>%
  summarise(total_count = sum(as.numeric(total_count)), .groups = 'drop') %>%
  pivot_wider(names_from = career_type, values_from = total_count, values_fill = 0) %>%
  rename_with(~ str_replace_all(., " ", "_"), everything()) %>%
  mutate(
    county_id = str_pad(as.numeric(sub("^US", "", county_id)), 5, pad = "0"),
    low_skilled_Y02E10_technologies = `9`, 
    mid_skilled_Y02E10_technologies = rowSums(select(., `4`, `5`, `6`, `7`, `8`), na.rm = TRUE),
    high_skilled_Y02E10_technologies = rowSums(select(., `1`, `2`, `3`), na.rm = TRUE),
    Y02E10_technologies_job_vacancies = rowSums(select(., `null`, `1`, `2`, `3`, `4`, `5`, `6`, `7`, `8`, `9`), na.rm = TRUE)
  )

Y02E10_employment_skill_type$year <- as.numeric(Y02E10_employment_skill_type$year)
Y02E10_employment_skill_type$month <- as.numeric(Y02E10_employment_skill_type$month)

Y02E10_employment_skill_type_quarterly <- Y02E10_employment_skill_type %>%
  select(county_id, year, month, Y02E10_technologies_job_vacancies, low_skilled_Y02E10_technologies, mid_skilled_Y02E10_technologies, high_skilled_Y02E10_technologies) %>%
  mutate(quarter = quarter(month)) %>%  # Convert month to quarter
  select(-month) %>%  # Remove the month column
  group_by(county_id, year, quarter) %>%  # Group by county_id, year, and quarter
  summarise(across(everything(), \(x) sum(x, na.rm = TRUE)), .groups = "drop")

Y02E10_employment_skill_type_quarterly$quarter <- str_pad(Y02E10_employment_skill_type_quarterly$quarter, 2, pad = "Q")

data <- left_join(data, Y02E10_employment_skill_type_quarterly, by = c("county_id", "year", "quarter"))
rm(Y02E10_employment_2017_18, Y02E10_employment_2019_20, Y02E10_employment_2021_22, Y02E10_employment_2023_24, Y02E10_employment_skill_type, Y02E10_employment_skill_type_quarterly, Y02E10_employment_2015_16, Y02E10_employment)
```

## Add Grey labor demand

```{r}
grey_employment_2015_16 <- read.csv("Data/lightcast data/Create_Grey_Dataset_2015_16.csv")
grey_employment_2017_18 <- read.csv("Data/lightcast data/Create_Grey_Dataset_2017_18.csv")
grey_employment_2019_20 <- read.csv("Data/lightcast data/Create_Grey_Dataset_2019_20.csv")
grey_employment_2021_22 <- read.csv("Data/lightcast data/Create_Grey_Dataset_2021_22.csv")
grey_employment_2023_24 <- read.csv("Data/lightcast data/Create_Grey_Dataset_2023_24.csv")

grey_employment <- rbind(grey_employment_2015_16, grey_employment_2017_18)
grey_employment <- rbind(grey_employment, grey_employment_2019_20)
grey_employment <- rbind(grey_employment, grey_employment_2021_22)
grey_employment <- rbind(grey_employment, grey_employment_2023_24)

grey_employment <- grey_employment %>%
  group_by(county_id, year, month) %>%
  summarise(grey_technologies_job_vacancies = sum(as.numeric(total_count)), .groups = 'drop')

grey_employment$year <- as.numeric(grey_employment$year)
grey_employment$month <- as.numeric(grey_employment$month)

grey_employment_quarterly <- grey_employment %>%
  select(county_id, year, month, grey_technologies_job_vacancies) %>%
  mutate(quarter = quarter(month)) %>%  # Convert month to quarter
  select(-month) %>%  # Remove the month column
  group_by(county_id, year, quarter) %>%  # Group by county_id, year, and quarter
  summarise(across(everything(), \(x) sum(x, na.rm = TRUE)), .groups = "drop")

grey_employment_quarterly$quarter <- str_pad(grey_employment_quarterly$quarter, 2, pad = "Q")
grey_employment_quarterly$county_id <- str_pad(as.numeric(sub("^US", "", grey_employment_quarterly$county_id)), 5, pad = "0")

data <- left_join(data, grey_employment_quarterly, by = c("county_id", "year", "quarter"))
rm(grey_employment_2017_18, grey_employment_2019_20, grey_employment_2021_22, grey_employment_2023_24, grey_employment, grey_employment_quarterly, grey_employment_2015_16)
```

## Add the total number of job vacancies

```{r}
employment <- read.csv("Data/lightcast data/Create_Total_Dataset.csv")
colnames(employment) <- employment[1, ]
employment <- employment[-1, ]

# 1. Clean and summarize total employment
employment_summary <- employment %>%
  group_by(county_id, year, month) %>%
  summarise(
    total_count = sum(as.numeric(total_count), na.rm = TRUE),
    .groups = 'drop'
  ) %>%
  mutate(
    county_id = str_pad(as.numeric(sub("^US", "", county_id)), 5, pad = "0")
  )

# How many job vacancies each year
employment_annual <- employment_summary %>% 
  select(year, total_count) %>%
  group_by(year) %>%
  summarise(total_count = sum(as.numeric(total_count), na.rm = TRUE))
solar_employment_annual <- left_join(solar_employment_annual, employment_annual, by = "year")
solar_employment_annual$solar_employment_percentage <- solar_employment_annual$total_count_solar / solar_employment_annual$total_count

# 2. Define skill level categories
high_skill <- c("Managers", "Professionals", "Technicians and Associate Professionals")
mid_skill <- c("Clerical Support Workers", "Service and Sales Workers", "Skilled Agricultural, Forestry and Fishery Workers", "Craft and Related Trades Workers", "Plant and Machine Operators, and Assemblers")
low_skill <- c("Elementary Occupations")

# 3. Create summaries for each skill level
high_skilled_jobs <- employment %>%
  filter(career_type %in% high_skill) %>%
  group_by(county_id, year, month) %>%
  summarise(high_skilled_jobs = sum(as.numeric(total_count), na.rm = TRUE), .groups = "drop") %>%
  mutate(county_id = str_pad(as.numeric(sub("^US", "", county_id)), 5, pad = "0"))

mid_skilled_jobs <- employment %>%
  filter(career_type %in% mid_skill) %>%
  group_by(county_id, year, month) %>%
  summarise(mid_skilled_jobs = sum(as.numeric(total_count), na.rm = TRUE), .groups = "drop") %>%
  mutate(county_id = str_pad(as.numeric(sub("^US", "", county_id)), 5, pad = "0"))

low_skilled_jobs <- employment %>%
  filter(career_type %in% low_skill) %>%
  group_by(county_id, year, month) %>%
  summarise(low_skilled_jobs = sum(as.numeric(total_count), na.rm = TRUE), .groups = "drop") %>%
  mutate(county_id = str_pad(as.numeric(sub("^US", "", county_id)), 5, pad = "0"))

# 4. Merge them all together
employment_combined <- employment_summary %>%
  left_join(high_skilled_jobs, by = c("county_id", "year", "month")) %>%
  left_join(mid_skilled_jobs, by = c("county_id", "year", "month")) %>%
  left_join(low_skilled_jobs, by = c("county_id", "year", "month")) %>%
  replace_na(list(high_skilled_jobs = 0, mid_skilled_jobs = 0, low_skilled_jobs = 0))

employment_combined$year <- as.numeric(employment_combined$year)
employment_combined$month <- as.numeric(employment_combined$month)

employment <- employment_combined %>%
  mutate(quarter = quarter(month)) %>%  # Convert month to quarter
  select(-month) %>%  # Remove the month column
  group_by(county_id, year, quarter) %>%  # Group by county_id, year, and quarter
  summarise(across(everything(), \(x) sum(x, na.rm = TRUE)), .groups = "drop")

employment$quarter <- str_pad(employment$quarter, 2, pad = "Q")

data <- left_join(data, employment, by = c("county_id", "year", "quarter"))

rm(employment, employment_combined, low_skilled_jobs, mid_skilled_jobs, high_skilled_jobs, employment_summary, low_skill, mid_skill, high_skill)
```

## Create neighboring spillover Bandwidths 2023-24 (cohort 1)

```{r}
counties <- sf::st_read("Data/raw data/tlgdb_2020_a_us_substategeo.gdb", layer = "County")
counties <- counties %>%
  select("GEOID") %>%
  rename("county_id" = "GEOID")
data <- left_join(data, counties, by = "county_id")

data <- st_as_sf(data)
data_temp <- data %>% filter(year == 2022 & quarter == "Q4") %>%
  select(county_id, ec_ind_official_cohort_1_percentage)
energy_communities <- data_temp[data_temp$ec_ind_official_cohort_1_percentage > 0, ]
non_energy_communities <- data_temp[data_temp$ec_ind_official_cohort_1_percentage == 0, ]

neighboring_counties <- st_touches(non_energy_communities, energy_communities)
neighboring_indices <- which(sapply(neighboring_counties, length) > 0)
non_energy_communities$neigboring_counties <- ifelse(row_number(non_energy_communities) %in% neighboring_indices, 1, 0)
neighboring_counties <- unique(non_energy_communities[non_energy_communities$neigboring_counties == 1, ]$county_id)
data_temp$neigboring_counties <- ifelse(data_temp$county_id %in% neighboring_counties, 1, 0)

previous_neighbors <- non_energy_communities[non_energy_communities$neigboring_counties == 1, ]
non_energy_communities <- non_energy_communities[non_energy_communities$neigboring_counties == 0, ]
neighboring_counties <- st_touches(non_energy_communities, previous_neighbors)
neighboring_indices <- which(sapply(neighboring_counties, length) > 0)
non_energy_communities$neigboring_counties <- ifelse(row_number(non_energy_communities) %in% neighboring_indices, 1, 0)
neighboring_counties <- unique(non_energy_communities[non_energy_communities$neigboring_counties == 1, ]$county_id)
data_temp$second_neigboring_counties <- ifelse(data_temp$county_id %in% neighboring_counties, 1, 0)

columns_of_interest <- c("neigboring_counties", "second_neigboring_counties")
data_temp <- data_temp %>%
  st_drop_geometry() 

data_temp$spillover_bandwidth <- apply(data_temp[columns_of_interest], 1, function(row) {
  colnames(data_temp[columns_of_interest])[which(row == 1)]
})

data_temp$spillover_bandwidth <- ifelse(data_temp$spillover_bandwidth %in% c("second_neigboring_counties", "neigboring_counties"), "neigboring_counties", "non_neigboring_counties")
data_temp$spillover_bandwidth <- ifelse(data_temp$ec_ind_official_cohort_1_percentage > 0, "energy_community", data_temp$spillover_bandwidth)
data_temp <- data_temp %>%
  select(-c("ec_ind_official_cohort_1_percentage"))

data_temp <- unique(data_temp)

data <- left_join(data, data_temp, by = "county_id")

data <- data %>%
  rename("spillover_bandwidth_neighbors_cohort_1" = "spillover_bandwidth")
```

## Create neighboring spillover Bandwidths 2023-24 (cohort 2)

```{r}
data <- st_as_sf(data)
data_temp <- data %>% filter(year == 2022 & quarter == "Q4") %>%
  select(county_id, ec_ind_official_cohort_2_percentage)
energy_communities <- data_temp[data_temp$ec_ind_official_cohort_2_percentage > 0, ]
non_energy_communities <- data_temp[data_temp$ec_ind_official_cohort_2_percentage == 0, ]

neighboring_counties <- st_touches(non_energy_communities, energy_communities)
neighboring_indices <- which(sapply(neighboring_counties, length) > 0)
non_energy_communities$neigboring_counties <- ifelse(row_number(non_energy_communities) %in% neighboring_indices, 1, 0)
neighboring_counties <- unique(non_energy_communities[non_energy_communities$neigboring_counties == 1, ]$county_id)
data_temp$neigboring_counties <- ifelse(data_temp$county_id %in% neighboring_counties, 1, 0)

previous_neighbors <- non_energy_communities[non_energy_communities$neigboring_counties == 1, ]
non_energy_communities <- non_energy_communities[non_energy_communities$neigboring_counties == 0, ]
neighboring_counties <- st_touches(non_energy_communities, previous_neighbors)
neighboring_indices <- which(sapply(neighboring_counties, length) > 0)
non_energy_communities$neigboring_counties <- ifelse(row_number(non_energy_communities) %in% neighboring_indices, 1, 0)
neighboring_counties <- unique(non_energy_communities[non_energy_communities$neigboring_counties == 1, ]$county_id)
data_temp$second_neigboring_counties <- ifelse(data_temp$county_id %in% neighboring_counties, 1, 0)

columns_of_interest <- c("neigboring_counties", "second_neigboring_counties")
data_temp <- data_temp %>%
  st_drop_geometry() 

data_temp$spillover_bandwidth <- apply(data_temp[columns_of_interest], 1, function(row) {
  colnames(data_temp[columns_of_interest])[which(row == 1)]
})

data_temp$spillover_bandwidth <- ifelse(data_temp$spillover_bandwidth %in% c("second_neigboring_counties", "neigboring_counties"), "neigboring_counties", "non_neigboring_counties")
data_temp$spillover_bandwidth <- ifelse(data_temp$ec_ind_official_cohort_2_percentage > 0, "energy_community", data_temp$spillover_bandwidth)
data_temp <- data_temp %>%
  select(-c("ec_ind_official_cohort_2_percentage"))

data_temp <- unique(data_temp)

data <- left_join(data, data_temp, by = "county_id")

data <- data %>%
  rename("spillover_bandwidth_neighbors_cohort_2" = "spillover_bandwidth")
```

## Create neighboring spillover Bandwidths 2024-25 (cohort 3)

```{r}
data <- st_as_sf(data)
data_temp <- data %>% filter(year == 2022 & quarter == "Q4") %>%
  select(county_id, ec_ind_official_cohort_3_percentage)
energy_communities <- data_temp[data_temp$ec_ind_official_cohort_3_percentage > 0, ]
non_energy_communities <- data_temp[data_temp$ec_ind_official_cohort_3_percentage == 0, ]

neighboring_counties <- st_touches(non_energy_communities, energy_communities)
neighboring_indices <- which(sapply(neighboring_counties, length) > 0)
non_energy_communities$neigboring_counties <- ifelse(row_number(non_energy_communities) %in% neighboring_indices, 1, 0)
neighboring_counties <- unique(non_energy_communities[non_energy_communities$neigboring_counties == 1, ]$county_id)
data_temp$neigboring_counties <- ifelse(data_temp$county_id %in% neighboring_counties, 1, 0)

previous_neighbors <- non_energy_communities[non_energy_communities$neigboring_counties == 1, ]
non_energy_communities <- non_energy_communities[non_energy_communities$neigboring_counties == 0, ]
neighboring_counties <- st_touches(non_energy_communities, previous_neighbors)
neighboring_indices <- which(sapply(neighboring_counties, length) > 0)
non_energy_communities$neigboring_counties <- ifelse(row_number(non_energy_communities) %in% neighboring_indices, 1, 0)
neighboring_counties <- unique(non_energy_communities[non_energy_communities$neigboring_counties == 1, ]$county_id)
data_temp$second_neigboring_counties <- ifelse(data_temp$county_id %in% neighboring_counties, 1, 0)

columns_of_interest <- c("neigboring_counties", "second_neigboring_counties")
data_temp <- data_temp %>%
  st_drop_geometry() 

data_temp$spillover_bandwidth <- apply(data_temp[columns_of_interest], 1, function(row) {
  colnames(data_temp[columns_of_interest])[which(row == 1)]
})

data_temp$spillover_bandwidth <- ifelse(data_temp$spillover_bandwidth %in% c("second_neigboring_counties", "neigboring_counties"), "neigboring_counties", "non_neigboring_counties")
data_temp$spillover_bandwidth <- ifelse(data_temp$ec_ind_official_cohort_3_percentage > 0, "energy_community", data_temp$spillover_bandwidth)
data_temp <- data_temp %>%
  select(-c("ec_ind_official_cohort_3_percentage"))

data_temp <- unique(data_temp)

data <- left_join(data, data_temp, by = "county_id")

data <- data %>%
  rename("spillover_bandwidth_neighbors_cohort_3" = "spillover_bandwidth")
```

## Create stata files

```{r}
# Create additional variables
data$year_quarter <- paste0(data$year, "-", data$quarter)
# Create treatment indicator
data$treatment <- ifelse(data$year_quarter %in% c("2023-Q1", "2023-Q2", "2023-Q3", "2023-Q4", "2024-Q1") & data$ec_ind_official_cohort_1_percentage > 0, 1, 0)
data$treatment <- ifelse(data$year_quarter %in% c("2024-Q2") & data$ec_ind_official_cohort_2_percentage > 0, 1, data$treatment)
data$treatment <- ifelse(data$year_quarter %in% c("2024-Q3", "2024-Q4") & data$ec_ind_official_cohort_3_percentage > 0, 1, data$treatment)

# Create binary EC variables
data$ec_ind_official_cohort_1 <- ifelse(data$ec_ind_official_cohort_1_percentage > 0, 1, 0)
data$ec_ind_official_cohort_2 <- ifelse(data$ec_ind_official_cohort_2_percentage > 0, 1, 0)
data$ec_ind_official_cohort_3 <- ifelse(data$ec_ind_official_cohort_3_percentage > 0, 1, 0)

# Create period variable
data$year <- as.numeric(data$year)
base_year <- min(data$year)  # Using the minimum year in the dataset
data$quarter_num <- as.numeric(substr(data$quarter, 2, 2))
data$period <- (data$year - base_year) * 4 + data$quarter_num

# Spillover dataset
data$spillover_treatment <- ifelse(data$spillover_bandwidth_neighbors_cohort_1 == "neigboring_counties" & data$year_quarter %in% c("2023-Q1", "2023-Q2", "2023-Q3", "2023-Q4", "2024-Q1"), 1, 0)
data$spillover_treatment <- ifelse(data$spillover_bandwidth_neighbors_cohort_2 == "neigboring_counties" & data$year_quarter %in% c("2024-Q2"), 1, data$spillover_treatment)
data$spillover_treatment <- ifelse(data$spillover_bandwidth_neighbors_cohort_3 == "neigboring_counties" & data$year_quarter %in% c("2024-Q3", "2024-Q4"), 1, data$spillover_treatment)

data <- data %>%
  mutate(across(c("solar_technologies_job_vacancies", "total_count", "Y02E10_technologies_job_vacancies", "wind_technologies_job_vacancies", "grey_technologies_job_vacancies"), ~replace_na(., 0)))
data$solar_technologies_job_vacancies_percentage <- data$solar_technologies_job_vacancies / data$total_count
data$wind_technologies_job_vacancies_percentage <- data$wind_technologies_job_vacancies / data$total_count
data$Y02E10_technologies_job_vacancies_percentage <- data$Y02E10_technologies_job_vacancies / data$total_count
data$grey_technologies_job_vacancies_percentage <- data$grey_technologies_job_vacancies / data$total_count

# Limit the size of the datasets
data_stata <- data %>%
  st_drop_geometry() %>%
  select(county_id, period, year, quarter, treatment, ec_ind_official_cohort_1, ec_ind_official_cohort_2, ec_ind_official_cohort_3, Y02E10_technologies_job_vacancies_percentage, solar_technologies_job_vacancies_percentage, wind_technologies_job_vacancies_percentage, grey_technologies_job_vacancies_percentage, total_count, spillover_treatment) %>%
  arrange(county_id, period)

write.csv(data_stata, "Data/constructed data/final_labor_demand_dataset_stata.csv")
```