---
title: "05_build_election_data"
author: "Joep Keuzenkamp"
date: "2025-01-10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Geographic regions

Here, we lay the groundwork by providing all the geographic regions in the dataset.

```{r}
# Add the census tracts
census_tracts <- sf::st_read("Data/raw data/tlgdb_2020_a_us_substategeo.gdb", layer = "Census_Tract")
census_tracts <- census_tracts %>%
  select("GEOID", "NAMELSAD", "SHAPE") %>%
  rename("census_tract_id" = "GEOID",
         "census_tract_name" = "NAMELSAD")
census_tracts$county_id <- str_sub(census_tracts$census_tract_id, 1, 5)
census_tracts$state_id <- str_sub(census_tracts$census_tract_id, 1, 2)
counties <- sf::st_read("Data/raw data/tlgdb_2020_a_us_substategeo.gdb", layer = "County")
counties <- counties %>%
  select("GEOID", "NAMELSAD") %>%
  rename("county_id" = "GEOID",
         "county_name" = "NAMELSAD") %>%
  st_drop_geometry()
census_tracts <- left_join(census_tracts, counties, by = "county_id")

rm(counties)
```

## Add the 2023 (cohort 1) energy communities: IRS notice 2023-29

```{r}
coal_closure <- read.csv("Data/raw data/IRA_Coal_Closure_Energy_Comm_2023v2/Coal_Closure_Energy_Communities_2023v2.csv")
coal_closure$geoid_tract_2020 <- str_pad(coal_closure$geoid_tract_2020, 11, pad = "0")
EC_employ <- read.csv("Data/raw data/MSA_NMSA_FEE_EC_Status_2023v2/MSA_NMSA_FFE_EC_2023v2.csv")
EC_employ$geoid_cty_2020 <- str_pad(EC_employ$geoid_cty_2020, 5, pad = "0")
coal_closure_mine <- coal_closure %>%
  filter(Tract_Status %in% c("is an energy community due to a coal mine closure"))
coal_closure_mine <- unique(coal_closure_mine$geoid_tract_2020)
coal_closure_generator <- coal_closure %>%
  filter(Generator_Closure == "Yes")
coal_closure_generator <- unique(coal_closure_generator$geoid_tract_2020)
coal_closure_adjacent <- coal_closure %>%
  filter(Adjacent_to_Closure == "Yes")
coal_closure_adjacent <- unique(coal_closure_adjacent$geoid_tract_2020)
EC_employ <- unique(EC_employ[EC_employ$EC_qual_status == "Yes", ]$geoid_cty_2020)

data <- census_tracts

data$coal_mine_closure_official_cohort_1 <- ifelse(data$census_tract_id %in% coal_closure_mine, 1, 0)
data$generator_closure_official_cohort_1 <- ifelse(data$census_tract_id %in% coal_closure_generator, 1, 0)
data$adjacent_closure_official_cohort_1 <- ifelse(data$census_tract_id %in% coal_closure_adjacent, 1, 0)
data$unemployment_official_msa_cohort_1 <- ifelse(data$county_id %in% EC_employ, 1, 0)

rm(coal_closure, EC_employ, coal_closure_adjacent, coal_closure_generator, coal_closure_mine)
```

## Add the 2023 (cohort 2) energy communities: IRS notice 2024-30

```{r}
coal_closure <- read.csv("Data/raw data/IRA_Coal_Closure_Energy_Comm_2023v2/Coal_Closure_Energy_Communities_2023v2.csv")
coal_closure$geoid_tract_2020 <- str_pad(coal_closure$geoid_tract_2020, 11, pad = "0")
EC_employ <- read.csv("Data/raw data/MSA_NMSA_EC_FFE_Status_v2023_3/MSA_NonMSA_EnergyCommunities_FossilFuelEmp_2023v3.csv")
EC_employ$geoid_county_2020 <- str_pad(EC_employ$geoid_county_2020, 5, pad = "0")
coal_closure_mine <- coal_closure %>%
  filter(Tract_Status %in% c("is an energy community due to a coal mine closure"))
coal_closure_mine <- unique(coal_closure_mine$geoid_tract_2020)
coal_closure_generator <- coal_closure %>%
  filter(Generator_Closure == "Yes")
coal_closure_generator <- unique(coal_closure_generator$geoid_tract_2020)
coal_closure_adjacent <- coal_closure %>%
  filter(Adjacent_to_Closure == "Yes")
coal_closure_adjacent <- unique(coal_closure_adjacent$geoid_tract_2020)
EC_employ <- unique(EC_employ[EC_employ$ec_qual_status == "Yes", ]$geoid_county_2020)

data$coal_mine_closure_official_cohort_2 <- ifelse(data$census_tract_id %in% coal_closure_mine, 1, 0)
data$generator_closure_official_cohort_2 <- ifelse(data$census_tract_id %in% coal_closure_generator, 1, 0)
data$adjacent_closure_official_cohort_2 <- ifelse(data$census_tract_id %in% coal_closure_adjacent, 1, 0)
data$unemployment_official_msa_cohort_2 <- ifelse(data$county_id %in% EC_employ, 1, 0)

rm(coal_closure, EC_employ, coal_closure_adjacent, coal_closure_generator, coal_closure_mine)
```

## Add the 2024 (cohort 3) energy communities: IRS notice 2024-48

```{r}
coal_closure <- read.csv("Data/raw data/Coal_Closures_EnergyComm_v2024_1/IRA_EnergyComm_CTracts_CoalClosures_v2024_1.csv")
coal_closure$geoid_tract_2020 <- str_pad(coal_closure$geoid_tract_2020, 11, pad = "0")
EC_employ <- read.csv("Data/raw data/MSA_NMSA_EC_FFE_v2024_1/MSA_NonMSA_EnergyCommunities_FossilFuelEmp_v2024_1.csv")
EC_employ$geoid_county_2020 <- str_pad(EC_employ$geoid_county_2020, 5, pad = "0")
coal_closure_mine <- coal_closure %>%
  filter(Mine_Closure == "Yes")
coal_closure_mine <- unique(coal_closure_mine$geoid_tract_2020)
coal_closure_generator <- coal_closure %>%
  filter(Generator_Closure == "Yes")
coal_closure_generator <- unique(coal_closure_generator$geoid_tract_2020)
coal_closure_adjacent <- coal_closure %>%
  filter(Adjacent_to_Closure == "Yes")
coal_closure_adjacent <- unique(coal_closure_adjacent$geoid_tract_2020)
EC_employ <- unique(EC_employ[EC_employ$ec_qual_status == "Yes", ]$geoid_county_2020)

data$coal_mine_closure_official_cohort_3 <- ifelse(data$census_tract_id %in% coal_closure_mine, 1, 0)
data$generator_closure_official_cohort_3 <- ifelse(data$census_tract_id %in% coal_closure_generator, 1, 0)
data$adjacent_closure_official_cohort_3 <- ifelse(data$census_tract_id %in% coal_closure_adjacent, 1, 0)
data$unemployment_official_msa_cohort_3 <- ifelse(data$county_id %in% EC_employ, 1, 0)

rm(coal_closure, EC_employ, coal_closure_adjacent, coal_closure_generator, coal_closure_mine)
```

## Add binary indicator for energy communities

```{r}
data <- data %>%
  mutate(ec_ind_official_cohort_1 = ifelse((coal_mine_closure_official_cohort_1 == 1 | 
                                   generator_closure_official_cohort_1 == 1 | 
                                   adjacent_closure_official_cohort_1 == 1) |
                                   unemployment_official_msa_cohort_1 == 1, 
                                   1, 0))

data <- data %>%
  mutate(ec_ind_official_cohort_2 = ifelse((coal_mine_closure_official_cohort_2 == 1 | 
                                   generator_closure_official_cohort_2 == 1 | 
                                   adjacent_closure_official_cohort_2 == 1) |
                                   unemployment_official_msa_cohort_2 == 1, 
                                   1, 0))

data <- data %>%
  mutate(ec_ind_official_cohort_3 = ifelse((coal_mine_closure_official_cohort_3 == 1 | 
                                   generator_closure_official_cohort_3 == 1 | 
                                   adjacent_closure_official_cohort_3 == 1) |
                                   unemployment_official_msa_cohort_3 == 1, 
                                   1, 0))
```

## Read in the datasets and prepare them

```{r}
## Land Surface Area
data <- st_as_sf(data)
data$area <- st_area(data)/1000

# We should have a row for each quarter-census tract combination
quarters <- seq.Date(from = as.Date("2000-01-01"), to = as.Date("2024-12-31"), by = "quarter")
census_tracts <- unique(data$census_tract_id)
all_combinations <- expand.grid(census_tract_id = census_tracts, quarter_date = quarters)
data <- merge(all_combinations, data, by = "census_tract_id", all.x = TRUE)
data$year <- substr(data$quarter_date, 1, 4)

rm(census_tracts, all_combinations, quarters)
```

## Add the Population by census tract

```{r}
population <- read.csv("Data/raw data/DECENNIALDP2020.DP1_2024-04-08T040530/DECENNIALDP2020.DP1-Data.csv")
population <- population[-1, ]
population <- subset(population, select = c("GEO_ID", "NAME", "DP1_0001C", "DP1_0006C", "DP1_0007C", "DP1_0008C", "DP1_0009C", "DP1_0010C", "DP1_0011C", "DP1_0012C", "DP1_0013C", "DP1_0014C"))
population <- population %>%
  rename("total_population_2020" = "DP1_0001C")
population$working_age_population_2020 <- as.numeric(population$DP1_0006C) + as.numeric(population$DP1_0007C) + as.numeric(population$DP1_0008C) + as.numeric(population$DP1_0009C) + as.numeric(population$DP1_0010C) + as.numeric(population$DP1_0011C) + as.numeric(population$DP1_0012C) + as.numeric(population$DP1_0013C) + as.numeric(population$DP1_0014C)
population$census_tract_id <- sub(".*US", "", population$GEO_ID)
population <- population %>%
  select(census_tract_id, total_population_2020, working_age_population_2020)

# Merge the demographics with the complete dataset
data <- left_join(data, population, by = "census_tract_id")

rm(population)
```

## Transform the dataframe so that we have counties as the basis

```{r}
data <- data %>%
  st_drop_geometry() %>%
  select(census_tract_id, county_id, county_name, state_id, ec_ind_official_cohort_1, ec_ind_official_cohort_2, ec_ind_official_cohort_3, area, year, total_population_2020, working_age_population_2020) %>% unique()
data$area <- as.numeric(data$area)
data$total_population_2020 <- as.numeric(data$total_population_2020)

data <- data %>%
  group_by(county_id, year) %>%
  summarise(county_name = first(county_name),
            state_id = first(state_id),
            ec_ind_official_cohort_1_percentage = mean(ec_ind_official_cohort_1, na.rm = TRUE),
            ec_ind_official_cohort_2_percentage = mean(ec_ind_official_cohort_2, na.rm = TRUE),
            ec_ind_official_cohort_3_percentage = mean(ec_ind_official_cohort_3, na.rm = TRUE),
            ec_ind_official_cohort_1_area_weighted = weighted.mean(ec_ind_official_cohort_1, area, na.rm = TRUE),
            ec_ind_official_cohort_2_area_weighted = weighted.mean(ec_ind_official_cohort_2, area, na.rm = TRUE),
            ec_ind_official_cohort_3_area_weighted = weighted.mean(ec_ind_official_cohort_3, area, na.rm = TRUE),
            ec_ind_official_cohort_1_population_weighted = weighted.mean(ec_ind_official_cohort_1, total_population_2020, na.rm = TRUE),
            ec_ind_official_cohort_2_population_weighted = weighted.mean(ec_ind_official_cohort_2, total_population_2020, na.rm = TRUE),
            ec_ind_official_cohort_3_population_weighted = weighted.mean(ec_ind_official_cohort_3, total_population_2020, na.rm = TRUE),
            ec_ind_official_cohort_1_working_population_weighted = weighted.mean(ec_ind_official_cohort_1, working_age_population_2020, na.rm = TRUE),
            ec_ind_official_cohort_2_working_population_weighted = weighted.mean(ec_ind_official_cohort_2, working_age_population_2020, na.rm = TRUE),
            ec_ind_official_cohort_3_working_population_weighted = weighted.mean(ec_ind_official_cohort_3, working_age_population_2020, na.rm = TRUE),
            area = sum(area, na.rm = TRUE),
            total_population_2020 = sum(total_population_2020, na.rm = TRUE),
            working_age_population_2020 = sum(working_age_population_2020, na.rm = TRUE))
```

# Presidential election

```{r}
# Let's add the election data
election <- read.csv("Data/raw data/countypres_2000-2024.csv")
election$county_fips <- as.character(election$county_fips)
election$county_fips <- str_pad(election$county_fips, 5, pad = "0")
election <- subset(election, select = c("year", "party", "candidatevotes", "totalvotes", "county_fips"))
unique_counties <- unique(election$county_fips)
unique_years <- unique(years <- unique(election$year))
all_combinations <- expand.grid(county_id = unique_counties, year = unique_years)
temp_data <- election %>% filter(party == "DEMOCRAT")
temp_data <- temp_data %>% 
  group_by(county_fips, year) %>%
  summarise(candidatevotes = sum(candidatevotes)) %>%
  rename("county_id" = "county_fips")
election_data <- left_join(all_combinations, temp_data, by = c("county_id", "year"))
election_data <- election_data %>%
  rename("democrat_votes_county" = "candidatevotes")
temp_data <- election %>% filter(party == "REPUBLICAN")
temp_data <- temp_data %>% 
  group_by(county_fips, year) %>%
  summarise(candidatevotes = sum(candidatevotes)) %>%
  rename("county_id" = "county_fips")
election_data <- left_join(election_data, temp_data, by = c("county_id", "year"))
election_data <- election_data %>%
  rename("republican_votes_county" = "candidatevotes")
temp_data <- election %>% filter(party %in% c("OTHER"))
temp_data <- temp_data %>% 
  group_by(county_fips, year) %>%
  summarise(candidatevotes = sum(candidatevotes)) %>%
  rename("county_id" = "county_fips")
election_data <- left_join(election_data, temp_data, by = c("county_id", "year"))
election_data <- election_data %>%
  rename("third_party_votes_county" = "candidatevotes")
election <- election %>%
  select(year, county_fips, totalvotes) %>%
  unique() %>%
  rename("county_id" = "county_fips",
         "total_votes_county" = "totalvotes")
election_data <- left_join(election_data, election, by = c("county_id", "year"))

election_data <- election_data %>%
  mutate(republican_voteshare_county = republican_votes_county / total_votes_county,
         democrat_voteshare_county = democrat_votes_county / total_votes_county,
         third_party_voteshare_county =  third_party_votes_county / total_votes_county)

# Merge with the total dataset
data$county_id <- str_pad(data$county_id, 5, pad = "0")
data$year <- as.numeric(data$year)
data <- left_join(data, election_data, by = c("county_id", "year"))

rm(election, election_data, temp_data, unique_counties, unique_years, years, all_combinations)

gc()
```

## Create a two-party vote share

```{r}
data$democrat_twoparty_voteshare_county <- data$democrat_votes_county / (data$democrat_votes_county + data$republican_votes_county)
data$republican_twoparty_voteshare_county <- data$republican_votes_county / (data$democrat_votes_county + data$republican_votes_county)
data <- data %>%
  filter(year %in% c(2000, 2004, 2008, 2012, 2016, 2020, 2024))
```

## Write the data file

```{r}
write.csv(data, "Data/constructed data/final_election_file.csv", row.names = FALSE)
```