---
title: "06_build_backenvelope_data"
output: html_document
date: "2025-09-03"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

## Geographic regions

```{r}
# Add the census tracts
census_tracts <- sf::st_read("Data/raw data/tlgdb_2020_a_us_substategeo.gdb", layer = "Census_Tract")
census_tracts <- census_tracts %>%
  select("GEOID", "NAMELSAD", "SHAPE") %>%
  rename("census_tract_id" = "GEOID",
         "census_tract_name" = "NAMELSAD")
census_tracts$county_id <- str_sub(census_tracts$census_tract_id, 1, 5)
census_tracts$state_id <- str_sub(census_tracts$census_tract_id, 1, 2)
counties <- sf::st_read("Data/raw data/tlgdb_2020_a_us_substategeo.gdb", layer = "County")
counties <- counties %>%
  select("GEOID", "NAMELSAD") %>%
  rename("county_id" = "GEOID",
         "county_name" = "NAMELSAD") %>%
  st_drop_geometry()
census_tracts <- left_join(census_tracts, counties, by = "county_id")

rm(counties)
```

## Add the 2023 (cohort 1) energy communities: IRS notice 2023-29

```{r}
coal_closure <- read.csv("Data/raw data/IRA_Coal_Closure_Energy_Comm_2023v2/Coal_Closure_Energy_Communities_2023v2.csv")
coal_closure$geoid_tract_2020 <- str_pad(coal_closure$geoid_tract_2020, 11, pad = "0")
EC_employ <- read.csv("Data/raw data/MSA_NMSA_FEE_EC_Status_2023v2/MSA_NMSA_FFE_EC_2023v2.csv")
EC_employ$geoid_cty_2020 <- str_pad(EC_employ$geoid_cty_2020, 5, pad = "0")
coal_closure_mine <- coal_closure %>%
  filter(Tract_Status %in% c("is an energy community due to a coal mine closure"))
coal_closure_mine <- unique(coal_closure_mine$geoid_tract_2020)
coal_closure_generator <- coal_closure %>%
  filter(Generator_Closure == "Yes")
coal_closure_generator <- unique(coal_closure_generator$geoid_tract_2020)
coal_closure_adjacent <- coal_closure %>%
  filter(Adjacent_to_Closure == "Yes")
coal_closure_adjacent <- unique(coal_closure_adjacent$geoid_tract_2020)
EC_employ <- unique(EC_employ[EC_employ$EC_qual_status == "Yes", ]$geoid_cty_2020)

data <- census_tracts

data$coal_mine_closure_official_cohort_1 <- ifelse(data$census_tract_id %in% coal_closure_mine, 1, 0)
data$generator_closure_official_cohort_1 <- ifelse(data$census_tract_id %in% coal_closure_generator, 1, 0)
data$adjacent_closure_official_cohort_1 <- ifelse(data$census_tract_id %in% coal_closure_adjacent, 1, 0)
data$unemployment_official_msa_cohort_1 <- ifelse(data$county_id %in% EC_employ, 1, 0)

rm(coal_closure, EC_employ, coal_closure_adjacent, coal_closure_generator, coal_closure_mine)
```

## Add the 2023 (cohort 2) energy communities: IRS notice 2024-30

```{r}
coal_closure <- read.csv("Data/raw data/IRA_Coal_Closure_Energy_Comm_2023v2/Coal_Closure_Energy_Communities_2023v2.csv")
coal_closure$geoid_tract_2020 <- str_pad(coal_closure$geoid_tract_2020, 11, pad = "0")
EC_employ <- read.csv("Data/raw data/MSA_NMSA_EC_FFE_Status_v2023_3/MSA_NonMSA_EnergyCommunities_FossilFuelEmp_2023v3.csv")
EC_employ$geoid_county_2020 <- str_pad(EC_employ$geoid_county_2020, 5, pad = "0")
coal_closure_mine <- coal_closure %>%
  filter(Tract_Status %in% c("is an energy community due to a coal mine closure"))
coal_closure_mine <- unique(coal_closure_mine$geoid_tract_2020)
coal_closure_generator <- coal_closure %>%
  filter(Generator_Closure == "Yes")
coal_closure_generator <- unique(coal_closure_generator$geoid_tract_2020)
coal_closure_adjacent <- coal_closure %>%
  filter(Adjacent_to_Closure == "Yes")
coal_closure_adjacent <- unique(coal_closure_adjacent$geoid_tract_2020)
EC_employ <- unique(EC_employ[EC_employ$ec_qual_status == "Yes", ]$geoid_county_2020)

data$coal_mine_closure_official_cohort_2 <- ifelse(data$census_tract_id %in% coal_closure_mine, 1, 0)
data$generator_closure_official_cohort_2 <- ifelse(data$census_tract_id %in% coal_closure_generator, 1, 0)
data$adjacent_closure_official_cohort_2 <- ifelse(data$census_tract_id %in% coal_closure_adjacent, 1, 0)
data$unemployment_official_msa_cohort_2 <- ifelse(data$county_id %in% EC_employ, 1, 0)

rm(coal_closure, EC_employ, coal_closure_adjacent, coal_closure_generator, coal_closure_mine)
```

## Add the 2024 (cohort 3) energy communities: IRS notice 2024-48

```{r}
coal_closure <- read.csv("Data/raw data/Coal_Closures_EnergyComm_v2024_1/IRA_EnergyComm_CTracts_CoalClosures_v2024_1.csv")
coal_closure$geoid_tract_2020 <- str_pad(coal_closure$geoid_tract_2020, 11, pad = "0")
EC_employ <- read.csv("Data/raw data/MSA_NMSA_EC_FFE_v2024_1/MSA_NonMSA_EnergyCommunities_FossilFuelEmp_v2024_1.csv")
EC_employ$geoid_county_2020 <- str_pad(EC_employ$geoid_county_2020, 5, pad = "0")
coal_closure_mine <- coal_closure %>%
  filter(Mine_Closure == "Yes")
coal_closure_mine <- unique(coal_closure_mine$geoid_tract_2020)
coal_closure_generator <- coal_closure %>%
  filter(Generator_Closure == "Yes")
coal_closure_generator <- unique(coal_closure_generator$geoid_tract_2020)
coal_closure_adjacent <- coal_closure %>%
  filter(Adjacent_to_Closure == "Yes")
coal_closure_adjacent <- unique(coal_closure_adjacent$geoid_tract_2020)
EC_employ <- unique(EC_employ[EC_employ$ec_qual_status == "Yes", ]$geoid_county_2020)

data$coal_mine_closure_official_cohort_3 <- ifelse(data$census_tract_id %in% coal_closure_mine, 1, 0)
data$generator_closure_official_cohort_3 <- ifelse(data$census_tract_id %in% coal_closure_generator, 1, 0)
data$adjacent_closure_official_cohort_3 <- ifelse(data$census_tract_id %in% coal_closure_adjacent, 1, 0)
data$unemployment_official_msa_cohort_3 <- ifelse(data$county_id %in% EC_employ, 1, 0)

rm(coal_closure, EC_employ, coal_closure_adjacent, coal_closure_generator, coal_closure_mine)
```

## Add binary indicator for energy communities

```{r}
data <- data %>%
  mutate(ec_ind_official_cohort_1 = ifelse((coal_mine_closure_official_cohort_1 == 1 | 
                                   generator_closure_official_cohort_1 == 1 | 
                                   adjacent_closure_official_cohort_1 == 1) |
                                   unemployment_official_msa_cohort_1 == 1, 
                                   1, 0))

data <- data %>%
  mutate(ec_ind_official_cohort_2 = ifelse((coal_mine_closure_official_cohort_2 == 1 | 
                                   generator_closure_official_cohort_2 == 1 | 
                                   adjacent_closure_official_cohort_2 == 1) |
                                   unemployment_official_msa_cohort_2 == 1, 
                                   1, 0))

data <- data %>%
  mutate(ec_ind_official_cohort_3 = ifelse((coal_mine_closure_official_cohort_3 == 1 | 
                                   generator_closure_official_cohort_3 == 1 | 
                                   adjacent_closure_official_cohort_3 == 1) |
                                   unemployment_official_msa_cohort_3 == 1, 
                                   1, 0))
```

## Load Solar Generator Data

```{r load_generators}
# Function to load quarterly generator data
load_generators <- function(file_path, year, quarter, existing_ids = NULL) {
  gens <- read_excel(file_path, skip = 2, sheet = "Planned") %>%
    filter(!is.na(Latitude), !is.na(Longitude)) %>%
    st_as_sf(coords = c("Longitude", "Latitude"), crs = 4326) %>%
    st_transform(crs = st_crs(census_tracts)) %>%
    mutate(
      ID = paste0(`Entity ID`, `Plant ID`),
      year = year,
      quarter = quarter
    ) %>%
    filter(Technology == "Solar Photovoltaic") %>%
    select(ID, `Nameplate Capacity (MW)`, year, quarter)
  
  # Filter out existing IDs if provided
  if (!is.null(existing_ids)) {
    gens <- gens %>% filter(!(ID %in% existing_ids))
  }
  
  return(gens)
}

# Load all quarterly data
quarters <- list(
  list(file = "january_generator2023.xlsx", year = 2023, quarter = "Q1"),
  list(file = "april_generator2023.xlsx", year = 2023, quarter = "Q2"),
  list(file = "july_generator2023.xlsx", year = 2023, quarter = "Q3"),
  list(file = "october_generator2023.xlsx", year = 2023, quarter = "Q4"),
  list(file = "january_generator2024.xlsx", year = 2024, quarter = "Q1"),
  list(file = "april_generator2024.xlsx", year = 2024, quarter = "Q2"),
  list(file = "july_generator2024.xlsx", year = 2024, quarter = "Q3"),
  list(file = "october_generator2024.xlsx", year = 2024, quarter = "Q4")
)

all_generators <- NULL
existing_ids <- c()

for (q in quarters) {
  gens <- load_generators(
    paste0("Data/raw data/eia_monthly_data/", q$file),
    q$year, q$quarter, existing_ids
  )
  all_generators <- rbind(all_generators, gens)
  existing_ids <- c(existing_ids, gens$ID)
}

cat("Total generators loaded:", nrow(all_generators), "\n")
```

## Process Solar Generators in Energy Communities

```{r filter_ec_generators}
# Join generators with EC data
all_generators <- st_join(
  all_generators,
  data %>% select(census_tract_id, ec_ind_official_cohort_1, ec_ind_official_cohort_2, ec_ind_official_cohort_3),
  join = st_within
) 

# Calculate mean per generator BEFORE aggregating (for verification)
mean_nameplate_per_generator <- all_generators %>%
  st_drop_geometry() %>%
  filter(
    (year == 2023 & ec_ind_official_cohort_1 == 1) |
    (year == 2024 & quarter %in% c("Q1") & ec_ind_official_cohort_1 == 1) |
    (year == 2024 & quarter %in% c("Q2") & ec_ind_official_cohort_2 == 1) |
    (year == 2024 & quarter %in% c("Q3", "Q4") & ec_ind_official_cohort_3 == 1)
  ) %>%
  pull(`Nameplate Capacity (MW)`) %>%
  mean(na.rm = TRUE)

cat("\n=== SOLAR GENERATORS IN ECs ===\n")
cat("Mean nameplate capacity per generator:", round(mean_nameplate_per_generator, 2), "MW\n")

# Aggregate to tract level with sum and count
generators_by_tract <- all_generators %>%
  st_drop_geometry() %>%
  filter(
    (year == 2023 & ec_ind_official_cohort_1 == 1) |
    (year == 2024 & quarter %in% c("Q1") & ec_ind_official_cohort_1 == 1) |
    (year == 2024 & quarter %in% c("Q2") & ec_ind_official_cohort_2 == 1) |
    (year == 2024 & quarter %in% c("Q3", "Q4") & ec_ind_official_cohort_3 == 1)
  ) %>%
  select(census_tract_id, `Nameplate Capacity (MW)`) %>%
  group_by(census_tract_id) %>%
  summarise(
    total_nameplate_capacity_mw = sum(`Nameplate Capacity (MW)`, na.rm = TRUE),
    n_generators = n()
  )

census_tracts <- left_join(data, generators_by_tract, by = "census_tract_id")

# Verify the weighted mean
verification_mean <- sum(census_tracts$total_nameplate_capacity_mw, na.rm = TRUE) / 
                     sum(census_tracts$n_generators, na.rm = TRUE)
cat("Verification (from tract data):", round(verification_mean, 2), "MW\n")
```

## Process Solar Investment in Energy Communities

```{r investment_analysis}
investment <- read.csv("Data/raw data/CIM/manufacturing_energy_and_industry_facility_metadata.csv", skip = 5) %>%
  mutate(
    Announcement_Date = as.Date(Announcement_Date),
    year = year(Announcement_Date),
    quarter = quarter(Announcement_Date),
    Estimated_Total_Facility_CAPEX = as.numeric(Estimated_Total_Facility_CAPEX),
    # Convert millions to actual dollars if needed
    Estimated_Total_Facility_CAPEX = Estimated_Total_Facility_CAPEX * 1e6
  ) %>%
  filter(
    year %in% c(2023, 2024),
    Segment == "Energy and Industry",
    Technology == "Solar"
  ) %>%
  rename(census_tract_id = census_tract_2020_geoid) %>%
  mutate(census_tract_id = str_pad(as.character(census_tract_id), 11, pad = "0")) 

# Join with EC data
investment <- left_join(
  investment, 
  data %>% select(census_tract_id, ec_ind_official_cohort_1, ec_ind_official_cohort_2, ec_ind_official_cohort_3) %>% st_drop_geometry(), 
  by = "census_tract_id"
) 

# Lets calculate how many investments were made in ECs
investment_temp <- investment %>%
  filter((ec_ind_official_cohort_1 == 1 & ((year == 2022 & quarter %in% c(1, 2)) | year == 2023 | (year == 2024 & quarter == 1))) |
           (ec_ind_official_cohort_2 == 1 & year == 2024 & quarter == 2) |
           (ec_ind_official_cohort_3 == 1 & year == 2024 & quarter %in% c(3, 4)))

# Calculate mean per facility BEFORE aggregating (for verification)
mean_capex_per_facility <- investment %>%
  filter(
    (year == 2023 & ec_ind_official_cohort_1 == 1) |
    (year == 2024 & quarter %in% c("Q1") & ec_ind_official_cohort_1 == 1) |
    (year == 2024 & quarter %in% c("Q2") & ec_ind_official_cohort_2 == 1) |
    (year == 2024 & quarter %in% c("Q3", "Q4") & ec_ind_official_cohort_3 == 1)
  ) %>%
  pull(Estimated_Total_Facility_CAPEX) %>%
  mean(na.rm = TRUE)

total_capex_all <- investment %>%
  filter(
    (year == 2023 & ec_ind_official_cohort_1 == 1) |
    (year == 2024 & quarter %in% c("Q1") & ec_ind_official_cohort_1 == 1) |
    (year == 2024 & quarter %in% c("Q2") & ec_ind_official_cohort_2 == 1) |
    (year == 2024 & quarter %in% c("Q3", "Q4") & ec_ind_official_cohort_3 == 1)
  ) %>%
  pull(Estimated_Total_Facility_CAPEX) %>%
  sum(na.rm = TRUE)

cat("\n=== SOLAR INVESTMENT IN ECs ===\n")
cat("Mean CAPEX per facility: $", format(mean_capex_per_facility, big.mark = ",", scientific = FALSE), "\n")
cat("Total CAPEX: $", format(total_capex_all, big.mark = ",", scientific = FALSE), "\n")

# Aggregate to tract level with sum and count
investment_by_tract <- investment %>%
  filter(
    (year == 2023 & ec_ind_official_cohort_1 == 1) |
    (year == 2024 & quarter %in% c("Q1") & ec_ind_official_cohort_1 == 1) |
    (year == 2024 & quarter %in% c("Q2") & ec_ind_official_cohort_2 == 1) |
    (year == 2024 & quarter %in% c("Q3", "Q4") & ec_ind_official_cohort_3 == 1)
  ) %>%
  select(census_tract_id, Estimated_Total_Facility_CAPEX) %>%
  group_by(census_tract_id) %>%
  summarise(
    total_capex = sum(Estimated_Total_Facility_CAPEX, na.rm = TRUE),
    n_investments = n()
  )

census_tracts <- left_join(census_tracts, investment_by_tract, by = "census_tract_id")

# Verify the weighted mean
verification_mean_capex <- sum(census_tracts$total_capex, na.rm = TRUE) / 
                           sum(census_tracts$n_investments, na.rm = TRUE)
cat("Verification (from tract data): $", format(verification_mean_capex, big.mark = ",", scientific = FALSE), "\n")
```

## Process Fossil Fuel Generators

```{r fossil_generators}
# Load fossil fuel generators (Q2 2022 baseline)
fossil_generators <- read_excel(
  "Data/raw data/eia_monthly_data/april_generator2022.xlsx",
  skip = 2
) %>%
  filter(
    Sector == "Electric Utility",
    !is.na(Latitude), !is.na(Longitude),
    Status == "(OP) Operating",
    Technology %in% c(
      "Natural Gas Steam Turbine", "Conventional Steam Coal",
      "Natural Gas Fired Combined Cycle", "Natural Gas Fired Combustion Turbine",
      "Petroleum Liquids", "Natural Gas Internal Combustion Engine",
      "Coal Integrated Gasification Combined Cycle", "Petroleum Coke",
      "Natural Gas with Compressed Air Storage", "Other Natural Gas"
    )
  ) %>%
  st_as_sf(coords = c("Longitude", "Latitude"), crs = 4326) %>%
  st_transform(crs = st_crs(census_tracts))

# Heat rates (Btu per kWh) from EIA
heat_rates <- list(
  coal = 10026, ng_steam = 10295, ng_turbine = 11030, ng_ic = 8894, ng_cc = 7596,
  petro_steam = 10263, petro_turbine = 13217, petro_ic = 10475, petro_cc = 9204
)

# Emission factors (kg CO2 per MMBtu)
emission_factors <- list(
  coal_bituminous = 93.28, coal_subbituminous = 97.17, coal_residential = 96.10,
  coal_lignite = 97.72, natural_gas = 52.91,
  petro_dfo = (73.96 + 75.04) / 2, petro_rfo = (72.93 + 75.10) / 2,
  petro_jf = 69.25, petro_ker = 75.20, petro_pc = 102.41,
  petro_pg = 62.87, petro_sgp = 66.88
)

# Capacity factors from EIA (2022 values)
capacity_factors_fossil <- list(
  coal = 0.484, ng_cc = 0.566, ng_turbine = 0.129, ng_steam = 0.156,
  ng_ic = 0.181, petro_steam = 0.132, petro_turbine = 0.016, petro_ic = 0.018
)

# Assign heat rates, emission factors, and capacity factors
fossil_generators <- fossil_generators %>%
  mutate(
    # Heat rates
    heat_rate = case_when(
      Technology %in% c("Conventional Steam Coal", "Coal Integrated Gasification Combined Cycle") ~ heat_rates$coal,
      Technology == "Natural Gas Steam Turbine" ~ heat_rates$ng_steam,
      Technology == "Natural Gas Fired Combined Cycle" ~ heat_rates$ng_cc,
      Technology == "Natural Gas Fired Combustion Turbine" ~ heat_rates$ng_turbine,
      Technology == "Natural Gas Internal Combustion Engine" ~ heat_rates$ng_ic,
      Technology == "Natural Gas with Compressed Air Storage" ~ heat_rates$ng_cc,
      Technology == "Other Natural Gas" ~ mean(c(heat_rates$ng_cc, heat_rates$ng_turbine, heat_rates$ng_steam, heat_rates$ng_ic)),
      Technology %in% c("Petroleum Liquids", "Petroleum Coke") & `Prime Mover Code` == "IC" ~ heat_rates$petro_ic,
      Technology %in% c("Petroleum Liquids", "Petroleum Coke") & `Prime Mover Code` %in% c("ST", "CA") ~ heat_rates$petro_steam,
      Technology %in% c("Petroleum Liquids", "Petroleum Coke") & `Prime Mover Code` %in% c("CT", "GT") ~ heat_rates$petro_turbine,
      TRUE ~ NA_real_
    ),
    # Emission factors
    emission_factor = case_when(
      Technology %in% c("Conventional Steam Coal", "Coal Integrated Gasification Combined Cycle") & `Energy Source Code` == "BIT" ~ emission_factors$coal_bituminous,
      Technology %in% c("Conventional Steam Coal", "Coal Integrated Gasification Combined Cycle") & `Energy Source Code` == "SUB" ~ emission_factors$coal_subbituminous,
      Technology %in% c("Conventional Steam Coal", "Coal Integrated Gasification Combined Cycle") & `Energy Source Code` == "RC" ~ emission_factors$coal_residential,
      Technology %in% c("Conventional Steam Coal", "Coal Integrated Gasification Combined Cycle") & `Energy Source Code` == "LIG" ~ emission_factors$coal_lignite,
      Technology %in% c("Conventional Steam Coal", "Coal Integrated Gasification Combined Cycle") & `Energy Source Code` == "SGC" ~ mean(c(emission_factors$coal_bituminous, emission_factors$coal_subbituminous, emission_factors$coal_residential, emission_factors$coal_lignite)),
      Technology %in% c("Natural Gas Steam Turbine", "Natural Gas Fired Combined Cycle", "Natural Gas Fired Combustion Turbine", "Natural Gas Internal Combustion Engine", "Natural Gas with Compressed Air Storage", "Other Natural Gas") ~ emission_factors$natural_gas,
      Technology %in% c("Petroleum Liquids", "Petroleum Coke") & `Energy Source Code` == "DFO" ~ emission_factors$petro_dfo,
      Technology %in% c("Petroleum Liquids", "Petroleum Coke") & `Energy Source Code` == "RFO" ~ emission_factors$petro_rfo,
      Technology %in% c("Petroleum Liquids", "Petroleum Coke") & `Energy Source Code` == "JF" ~ emission_factors$petro_jf,
      Technology %in% c("Petroleum Liquids", "Petroleum Coke") & `Energy Source Code` == "KER" ~ emission_factors$petro_ker,
      Technology %in% c("Petroleum Liquids", "Petroleum Coke") & `Energy Source Code` == "PC" ~ emission_factors$petro_pc,
      Technology %in% c("Petroleum Liquids", "Petroleum Coke") & `Energy Source Code` == "PG" ~ emission_factors$petro_pg,
      Technology %in% c("Petroleum Liquids", "Petroleum Coke") & `Energy Source Code` == "SGP" ~ emission_factors$petro_sgp,
      TRUE ~ NA_real_
    ),
    # Capacity factors
    capacity_factor = case_when(
      Technology %in% c("Conventional Steam Coal", "Coal Integrated Gasification Combined Cycle") ~ capacity_factors_fossil$coal,
      Technology == "Natural Gas Steam Turbine" ~ capacity_factors_fossil$ng_steam,
      Technology == "Natural Gas Fired Combined Cycle" ~ capacity_factors_fossil$ng_cc,
      Technology == "Natural Gas Fired Combustion Turbine" ~ capacity_factors_fossil$ng_turbine,
      Technology == "Natural Gas Internal Combustion Engine" ~ capacity_factors_fossil$ng_ic,
      Technology == "Natural Gas with Compressed Air Storage" ~ capacity_factors_fossil$ng_cc,
      Technology == "Other Natural Gas" ~ mean(c(capacity_factors_fossil$ng_cc, capacity_factors_fossil$ng_turbine, capacity_factors_fossil$ng_steam, capacity_factors_fossil$ng_ic)),
      Technology %in% c("Petroleum Liquids", "Petroleum Coke") & `Prime Mover Code` == "GT" ~ capacity_factors_fossil$petro_turbine,
      Technology %in% c("Petroleum Liquids", "Petroleum Coke") & `Prime Mover Code` == "IC" ~ capacity_factors_fossil$petro_ic,
      Technology %in% c("Petroleum Liquids", "Petroleum Coke") & `Prime Mover Code` %in% c("ST", "CA") ~ capacity_factors_fossil$petro_steam,
      Technology %in% c("Petroleum Liquids", "Petroleum Coke") & `Prime Mover Code` == "CT" ~ capacity_factors_fossil$petro_turbine,
      TRUE ~ NA_real_
    ),
    # Calculate emissions
    kg_CO2_MWh = (heat_rate / 1000) * emission_factor,
    annual_MWh = `Nameplate Capacity (MW)` * capacity_factor * 8760,
    annual_tCO2 = annual_MWh * kg_CO2_MWh / 1000
  )

cat("\n=== FOSSIL FUEL GENERATORS ===\n")
cat("Total fossil generators loaded:", nrow(fossil_generators), "\n")
```

## Aggregate Fossil Generators to Census Tracts

```{r fossil_ec}
# Join with census tracts
fossil_generators <- st_join(
  fossil_generators,
  census_tracts %>% select(census_tract_id),
  join = st_within
)

# Aggregate to tract level
fossil_by_tract <- fossil_generators %>%
  st_drop_geometry() %>%
  select(census_tract_id, annual_tCO2, annual_MWh) %>%
  group_by(census_tract_id) %>%
  summarise(
    annual_tCO2 = sum(annual_tCO2, na.rm = TRUE),
    annual_MWh = sum(annual_MWh, na.rm = TRUE)
  )

census_tracts <- left_join(census_tracts, fossil_by_tract, by = "census_tract_id")

# Calculate weighted CO2 intensity for ECs
ec_fossil_stats <- census_tracts %>%
  filter((ec_ind_official_cohort_1 == 1 | ec_ind_official_cohort_2 == 1 | ec_ind_official_cohort_3 == 1) & !is.na(annual_MWh) & annual_MWh > 0) %>%
  st_drop_geometry() %>%
  summarise(
    total_tCO2 = sum(annual_tCO2, na.rm = TRUE),
    total_MWh = sum(annual_MWh, na.rm = TRUE),
    weighted_co2_intensity = total_tCO2 / total_MWh
  )

cat("Weighted CO2 intensity in ECs:", round(ec_fossil_stats$weighted_co2_intensity, 4), "tCO2/MWh\n")
```

## Write dataset to stata

```{r}
census_tracts <- census_tracts %>%
  st_drop_geometry() %>%
  select(census_tract_id,
         county_id,
    ec_ind_official_cohort_1,
    ec_ind_official_cohort_2,
    ec_ind_official_cohort_3,
    total_nameplate_capacity_mw,
    n_generators,
    total_capex,
    n_investments,
    annual_tCO2,
    annual_MWh)

# Write to CSV
write.csv(
  census_tracts,
  "Data/constructed data/back_envelope_panel_A.csv",
  row.names = FALSE
)
```

## Add Job Vacancy Data

```{r job_analysis}
labor_data <- read.csv(
  "C:/Users/Keuze001/Dropbox/IRA reproducibility package/Data/constructed data/final_labor_demand_dataset_stata.csv"
) %>%
  filter(
    (year == 2023 & ec_ind_official_cohort_1 == 1) |
    (year == 2024 & quarter %in% c("Q1") & ec_ind_official_cohort_1 == 1) |
    (year == 2024 & quarter %in% c("Q2") & ec_ind_official_cohort_2 == 1) |
    (year == 2024 & quarter %in% c("Q3", "Q4") & ec_ind_official_cohort_3 == 1)
  ) %>%
  mutate(
    number_solar_vacancies = solar_technologies_job_vacancies_percentage * total_count,
    county_id = str_pad(as.character(county_id), 5, pad = "0")
  ) %>%
  select(number_solar_vacancies, county_id) %>%
  group_by(county_id) %>%
  summarise(number_solar_vacancies = sum(number_solar_vacancies, na.rm = TRUE))

counties <- census_tracts %>%
  select(total_capex, county_id) %>%
  group_by(county_id) %>%
  summarise(total_capex = sum(total_capex, na.rm = TRUE))

counties <- left_join(counties, labor_data, by = "county_id")
```

## Export Final Dataset

```{r export}
# Write to CSV
write.csv(
  counties,
  "Data/constructed data/back_envelope_panel_B.csv",
  row.names = FALSE
)
```